---
title: "Appendix models"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(interactions)
library(stargazer)
library(fastDummies)
library(geepack)
library(survey)
library(ipw)
library(WeightIt)
library(reshape)
library(CMAverse)
#full.data <- read.csv("cleaned data full all years_v2.csv")

full.data <- read.csv("coefs with city covariates cleaned.csv")
precincts_total <- read.csv("n_precincts_all.csv")

#absentee <- read.csv("absentee coefficients.csv")
#absentee <- absentee %>% dplyr::select(pct.absentee, city_id_year)
#full.data <- merge(full.data, absentee, by = "city_id_year")

#Note: Missing cities are manually added to full.data file

full.data <- full.data %>% mutate(presidential = ifelse(year.x == 2004 | year.x == 2008 | year.x == 2012, 1, 0))
full.data <- full.data %>% mutate(known.opp.mayor = ifelse(is.na(opp_mayor1) == T, 0, ifelse(opp_mayor1==1, 1,0)))
full.data <- full.data %>% mutate(appointed.exec = ifelse(is.na(cancel.year)==T, 0, ifelse(year.x >= cancel.year, 1, 0)))
full.data <- full.data %>% dplyr::rename(turnout.coef = turnout)

full.data <- full.data %>% mutate(years.with.elections = ifelse(is.na(cancel.year)==T, year.x-1996, ifelse(year.x - cancel.year < 0, year.x - 1996, cancel.year - 1996))) #This gives a measure of early vs late vs. control; 1996 bc this is when local elections first took place 

full.data <- full.data %>% mutate(years.post.treatment = ifelse(is.na(cancel.year)==T, 0, ifelse(year.x - cancel.year < 0, 0, year.x - cancel.year)))
full.data <- full.data %>% mutate(years.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2007 & year.x ==2007, 1, years.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.
full.data <- full.data %>% mutate(years.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2011 & year.x ==2011, 1, years.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.

full.data <- full.data %>% mutate(treated.post.treatment = ifelse(is.na(cancel.year)==T, 0, ifelse(year.x - cancel.year < 0, 0, 1)))
full.data <- full.data %>% mutate(treated.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2007 & year.x ==2007, 1, treated.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.
full.data <- full.data %>% mutate(treated.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2011 & year.x ==2011, 1, treated.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.


full.data <- full.data %>% mutate(years.under.appt = ifelse(is.na(cancel.year) == T, 0, ifelse(year.x - cancel.year < 0, 0, ifelse(year.x == 2007 | year.x == 2011 & year.x == cancel.year, 1, year.x - cancel.year))))

full.data <- full.data %>% mutate(city_id_factor = as.factor(city_id))


full.data <- full.data %>% mutate(treatment.group = ifelse(is.na(cancel.year)==F, 1, 0))

full.data <- full.data %>% mutate(control = ifelse(is.na(cancel.year)==T, 1, 0))
full.data <- full.data %>% mutate(early.treated = ifelse(is.na(cancel.year)==F & cancel.year <= 2007, 1, 0))
full.data <- full.data %>% mutate(late.treated = ifelse(is.na(cancel.year)==F & cancel.year > 2007, 1, 0))


full.data <- full.data %>% mutate(years.under.regime = ifelse(appointed.exec == 0, year.x - 2000, year.x - cancel.year))

##Dummies for ethnic categorical

full.data <- dummy_cols(full.data, select_columns = "ethnic.categorical")
full.data <- full.data %>% dplyr::rename(majority.russian.republic = ethnic.categorical_Majority_Russian_republic)
full.data <- full.data %>% dplyr::rename(majority.minority.republic = `ethnic.categorical_Majority-minority_republic`)

##Lagged treatments
###Note: go into earlier data frame and lag by year, not by period

full.data <- full.data %>% mutate(cancel.year.mod = ifelse(is.na(cancel.year)==T, NA, ifelse(is.na(cancel.year)==F & cancel.year != 2008 & cancel.year != 2012, cancel.year, cancel.year + 1)))

full.data <- full.data %>% mutate(treated.mod = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.1lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 1, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.2lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 2, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.3lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 3, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.4lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 4, 1, 0)))


##Lagged DVs

full.data <- full.data %>% group_by(city_id) %>% mutate(turncoef.1lag = lag(turnout.coef))
full.data <- full.data %>% group_by(city_id) %>% mutate(turncoef.2lag = lag(turnout.coef, 2))

full.data <- full.data %>% group_by(city_id) %>% mutate(urvoteshare.1lag = lag(ur.voteshare))
full.data <- full.data %>% group_by(city_id) %>% mutate(urvoteshare.2lag = lag(ur.voteshare, 2))

##Elections since treatment

full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(cancel.year.mod <= 2007 & year.x == 2008, 1, ifelse(cancel.year.mod <= 2007 & year.x == 2011, 2, ifelse(cancel.year.mod <= 2007 & year.x == 2012, 3, NA)))))

full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(elex.since.treatment) == F, elex.since.treatment, 
                                  ifelse(cancel.year.mod == 2008 & year.x < 2011, 0, 
                                  ifelse(cancel.year.mod == 2008 & year.x == 2011, 1,
                                  ifelse(cancel.year.mod == 2008 & year.x == 2012, 2, elex.since.treatment)))))


full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(elex.since.treatment) == F, elex.since.treatment, 
                                  ifelse(cancel.year.mod > 2008 & cancel.year.mod <= 2011 & year.x <= 2011, 0, 
                                  ifelse(cancel.year.mod > 2008 & cancel.year.mod <= 2011 & year.x == 2012, 1,  elex.since.treatment))))


full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(elex.since.treatment) == F, elex.since.treatment, 0))

##Region id as factor

full.data <- full.data %>% mutate(regionid.ch = as.factor(regionid.ch))

##Adding n_precincts

precincts_total <- precincts_total %>% mutate(city_id_year = paste(city_id, year, sep = "_"))
precincts_total <- precincts_total %>% dplyr::select(-year, -city_id)

full.data <- left_join(full.data, precincts_total, by ="city_id_year")

full.data <- full.data %>% dplyr::rename(n.precincts = n)

##Share of appointed mayors nationwide

full.data <- full.data %>% group_by(year.x) %>% mutate(total.appointed = sum(appointed.exec, na.rm=T))
full.data <- full.data %>% group_by(year.x) %>% mutate(total.cities = length(unique(city_id)))
full.data <- full.data %>% mutate(appointed.share = total.appointed/total.cities)

##Lagged share

full.data <- full.data %>% group_by(city_id) %>% mutate(appointed.share.lag = lag(appointed.share))
full.data <- full.data %>% mutate(appointed.share.lag = ifelse(year.x == 2003, 0, appointed.share.lag))

```


##Descriptive statistics for OLS models

```{r}
full.data.descrip <- full.data %>% dplyr::select(turnout.coef, ur.voteshare, presidential, xconst.lag, putin.app.3mo, urgov,             mayor.tenure, lnAvgSalary, dem, comp.scale2, known.opp.mayor, margin.most.recent, appointed.share, n.precincts,  appointed.exec, years.under.regime)

modelsummary::datasummary_skim(full.data.descrip %>% dplyr::select(-city_id), output = "appendix_descriptive_stats.html")
```





##IPW 

```{r}
##Note: including urvoteshare and/or turnoutcoef worsens balance on those variables, so they are excluded

covariates <- full.data %>% select(city_id, presidential, xconst.lag, putin.app.3mo, urgov, mayor.tenure, lnAvgSalary, dem, comp.scale2, known.opp.mayor, margin.most.recent, year.x, treated.mod, turnout.coef, years.under.regime, ur.voteshare , treated.mod.1lag, treated.mod.2lag, treated.mod.3lag, years.with.elections, urvoteshare.1lag, turncoef.1lag, prior.treat.cities.region)
                                   
complete.tf <- complete.cases(covariates)
covariates <- bind_cols(covariates, complete.tf)
covariates <- covariates %>% dplyr::rename(complete.tf = ...24)

covariates <- covariates %>% filter(complete.tf == T)

data_long_sort <- covariates %>% dplyr::arrange(city_id, year.x)
data_long_sort <- data_long_sort %>% dplyr::select(-complete.tf)
data_long_sort <- data.frame(data_long_sort)

w <- ipwtm(
  exposure = treated.mod,
  family = "binomial",
  link = "logit",
  numerator = ~ treated.mod.1lag + treated.mod.2lag,
  denominator = ~ treated.mod.1lag + treated.mod.2lag + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent +  dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
  id = city_id,
  timevar=year.x,
  type="first",
  data = data_long_sort)
summary(w$ipw.weights)
```



```{r}
iptw = w$ipw.weights


# Add the iptw variable onto a new dataframe = data2.
data2 <- cbind(data_long_sort, iptw)

##Truncated weights .95

data2 <- data2 %>% mutate(tsw = ifelse(iptw < quantile(iptw, probs=.05), quantile(iptw, probs=.05), iptw))

data2 <- data2 %>% mutate(tsw = ifelse(iptw > quantile(iptw, probs=.95), quantile(iptw, probs=.95), tsw))

summary(data2$tsw)
```
##Treated cities within regions

```{r}
###########################################################################################
# GEE model #2 - IPTW fitted to MSM with clustered robust SE
###########################################################################################
########################################################################
gee.iptw <- geeglm(turnout.coef~ treated.mod*prior.treat.cities.region + treated.mod.1lag + treated.mod.2lag + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + cluster(city_id) + prior.treat.cities.region,
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw)
#m1 <- broom::tidy(gee.iptw)
#pixiedust::dust(m1) %>%
#  pixiedust::sprinkle_print_method("html")


gee.iptw2 <- geeglm(ur.voteshare~ treated.mod*prior.treat.cities.region + treated.mod.1lag + treated.mod.2lag +  presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + turnout.coef + cluster(city_id) + prior.treat.cities.region,
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw2)

#m2 <- broom::tidy(gee.iptw2)
#pixiedust::dust(m2) %>%
#  pixiedust::sprinkle_print_method("html")

sjPlot::tab_model(gee.iptw, gee.iptw2, show.ci = F, p.style = "stars", digits = 3, show.se = T, collapse.se =  T)

```

##Including mayor tenure interaction

```{r}

```


##IPW excluding 2003 and 2004 (treatment not possible)

```{r}
##Note: including urvoteshare and/or turnoutcoef worsens balance on those variables, so they are excluded

covariates <- full.data %>% select(city_id, presidential, xconst.lag, putin.app.3mo, urgov, mayor.tenure, lnAvgSalary, dem, comp.scale2, known.opp.mayor, margin.most.recent, year.x, treated.mod, turnout.coef, years.under.regime, ur.voteshare , treated.mod.1lag, treated.mod.2lag, treated.mod.3lag, years.with.elections, urvoteshare.1lag, turncoef.1lag, prior.treat.cities.region)
covariates <- covariates %>% filter(year.x > 2004)
                                   
complete.tf <- complete.cases(covariates)
covariates <- bind_cols(covariates, complete.tf)
covariates <- covariates %>% dplyr::rename(complete.tf = ...24)

covariates <- covariates %>% filter(complete.tf == T)

data_long_sort <- covariates %>% dplyr::arrange(city_id, year.x)
data_long_sort <- data_long_sort %>% dplyr::select(-complete.tf)
data_long_sort <- data.frame(data_long_sort)

w <- ipwtm(
  exposure = treated.mod,
  family = "binomial",
  link = "logit",
  numerator = ~ treated.mod.1lag + treated.mod.2lag,
  denominator = ~ treated.mod.1lag + treated.mod.2lag + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent +  dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
  id = city_id,
  timevar=year.x,
  type="first",
  data = data_long_sort)
summary(w$ipw.weights)
```



```{r}
iptw = w$ipw.weights


# Add the iptw variable onto a new dataframe = data2.
data2 <- cbind(data_long_sort, iptw)

##Truncated weights .95

data2 <- data2 %>% mutate(tsw = ifelse(iptw < quantile(iptw, probs=.05), quantile(iptw, probs=.05), iptw))

data2 <- data2 %>% mutate(tsw = ifelse(iptw > quantile(iptw, probs=.95), quantile(iptw, probs=.95), tsw))

summary(data2$tsw)
```

```{r}
###########################################################################################
# GEE model #2 - IPTW fitted to MSM with clustered robust SE
###########################################################################################
########################################################################
gee.iptw <- geeglm(turnout.coef~ treated.mod + treated.mod.1lag + treated.mod.2lag + presidential + 
                     putin.app.3mo + mayor.tenure + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw)
#m1 <- broom::tidy(gee.iptw)
#pixiedust::dust(m1) %>%
#  pixiedust::sprinkle_print_method("html")


gee.iptw2 <- geeglm(ur.voteshare~ treated.mod + treated.mod.1lag + treated.mod.2lag +  presidential + 
                     putin.app.3mo + mayor.tenure + turnout.coef + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw2)

#m2 <- broom::tidy(gee.iptw2)
#pixiedust::dust(m2) %>%
#  pixiedust::sprinkle_print_method("html")

sjPlot::tab_model(gee.iptw, gee.iptw2, show.ci = F, p.style = "stars", digits = 3, show.se = T, collapse.se =  T)

```

##CBPS weights using WeightIt

To do this, need to capture the full treatment history. I.e. tx1 = 1 if treated in 2003, tx2 = 1 if treated in 2004

geeglm doesn't work for the CBPS weights, but a basic lm does. Need to make sure that is acceptable.

For now, this is *excluded* from robustness checks. Weights are highly unstable (see summary(W) for each option. Results in high coefficients of variaton and small weighted sample sizes)

```{r}
#full.data <- full.data %>% mutate(tx1 = 0)
full.data <- full.data %>% mutate(tx2 = 0)
full.data <- full.data %>% mutate(tx3 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2007, 1, 0)))
full.data <- full.data %>% mutate(tx4 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2007, 1, 0)))
full.data <- full.data %>% mutate(tx5 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2011, 1, 0)))
full.data <- full.data %>% mutate(tx6 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2011, 1, 0)))


covariates <- full.data %>% dplyr::select(tx2, tx3, tx4, tx5, tx6, urgov, lnAvgSalary, comp.scale2, known.opp.mayor, margin.most.recent, dem, years.with.elections, turnout.coef, ur.voteshare, presidential, xconst.lag,
                     putin.app.3mo, mayor.tenure, years.under.appt,  urvoteshare.1lag, turncoef.1lag, cancel.year.mod)
covariates <- covariates %>% mutate(cancel.year.mod = ifelse(is.na(cancel.year.mod)==T, 0, cancel.year.mod))
complete.tf <- complete.cases(covariates)
covariates <- bind_cols(covariates, complete.tf)
covariates <- covariates %>% dplyr::rename(complete.tf = ...24)

covariates <- covariates %>% filter(complete.tf == T)

```

```{r}
covariates <- fastDummies::dummy_cols(covariates, select_columns = "cancel.year.mod")
```

Treatment by period option
```{r}
W <- weightitMSM(list(tx3 ~ tx2 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                      #tx2 ~ tx1 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections,
                    
                      tx4 ~ tx3 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                      tx5 ~  tx4 + tx3  + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                      tx6 ~ tx3 + tx4 + tx5 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag),
                 method = "cbps",
                      data = covariates)
weights <- W$weights
covariates <- bind_cols(covariates, weights)
covariates <- covariates %>% dplyr::rename(cbps.weights = ...34)

```


```{r}

########################################################################
cbps.lm1 <- lm(turnout.coef~ tx3 + tx5 + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure,
                    data=covariates, 
                     weights=cbps.weights)
summary(cbps.lm1)
#m1 <- broom::tidy(gee.iptw)
#pixiedust::dust(m1) %>%
#  pixiedust::sprinkle_print_method("html")


cbps.lm2 <- lm(ur.voteshare~ tx3 + tx5 +  presidential + xconst.lag + 
                     putin.app.3mo + mayor.tenure +  turnout.coef,
                     data=covariates, 
                        weights=cbps.weights)
summary(cbps.lm2)

#m2 <- broom::tidy(gee.iptw2)
#pixiedust::dust(m2) %>%
#  pixiedust::sprinkle_print_method("html")

sjPlot::tab_model(gee.iptw, gee.iptw2, show.ci = F, p.style = "stars", digits = 3, show.se = T, collapse.se =  T)

```
Treatment by year option. Note this is probably incorrect, since it shows the effect of being in a treatment group, rather than the effect of having received a treatment

```{r}
W <- weightitMSM(list(cancel.year.mod_2004 ~ urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                      #tx2 ~ tx1 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections,
                    
                      cancel.year.mod_2005 ~ cancel.year.mod_2004 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                      cancel.year.mod_2006 ~ cancel.year.mod_2005 +cancel.year.mod_2004  + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                      cancel.year.mod_2007 ~ cancel.year.mod_2006 + cancel.year.mod_2005 +cancel.year.mod_2004 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                 cancel.year.mod_2009 ~  cancel.year.mod_2007 + cancel.year.mod_2006 + cancel.year.mod_2005 +cancel.year.mod_2004 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                 cancel.year.mod_2010 ~ cancel.year.mod_2009 +  cancel.year.mod_2007 + cancel.year.mod_2006 + cancel.year.mod_2005 +cancel.year.mod_2004 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
                  cancel.year.mod_2011 ~ cancel.year.mod_2010 + cancel.year.mod_2009 +  cancel.year.mod_2007 + cancel.year.mod_2006 + cancel.year.mod_2005 +cancel.year.mod_2004 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag
                      ),
                 method = "cbps",
                      data = covariates)
weights <- W$weights
covariates <- bind_cols(covariates, weights)
covariates <- covariates %>% dplyr::rename(cbps.weights2 = ...35)

```

```{r}

########################################################################
cbps.lm1 <- lm(turnout.coef~ cancel.year.mod_2011 + cancel.year.mod_2010 + cancel.year.mod_2009 +  cancel.year.mod_2007 + cancel.year.mod_2006 + cancel.year.mod_2005 +cancel.year.mod_2004 + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure,
                    data=covariates, 
                     weights=cbps.weights2)
summary(cbps.lm1)
#m1 <- broom::tidy(gee.iptw)
#pixiedust::dust(m1) %>%
#  pixiedust::sprinkle_print_method("html")


cbps.lm2 <- lm(ur.voteshare~ cancel.year.mod_2011 + cancel.year.mod_2010 + cancel.year.mod_2009 +  cancel.year.mod_2007 + cancel.year.mod_2006 + cancel.year.mod_2005 +cancel.year.mod_2004 +  presidential + xconst.lag + 
                     putin.app.3mo + mayor.tenure + turnout.coef,
                     data=covariates, 
                        weights=cbps.weights2)
summary(cbps.lm2)

#m2 <- broom::tidy(gee.iptw2)
#pixiedust::dust(m2) %>%
#  pixiedust::sprinkle_print_method("html")

sjPlot::tab_model(gee.iptw, gee.iptw2, show.ci = F, p.style = "stars", digits = 3, show.se = T, collapse.se =  T)
```

#OLS model interacting with mayor tenure
Currently not run, since mayor tenure is included as control in main models

Effect of transitions within both regime types

```{r}
full.data <- full.data %>% mutate(mayor.tenure.sq = mayor.tenure^2)

model.tc.tenure <- lm(turnout.coef ~ city_id_factor + presidential + xconst.lag + putin.app.3mo +  urgov + 
                  lnAvgSalary + dem + comp.scale2  + known.opp.mayor + appointed.exec*mayor.tenure + appointed.exec*mayor.tenure.sq, data = full.data)

sjPlot::plot_model(model.tc.tenure, type = "pred", terms = c("mayor.tenure", "mayor.tenure.sq", "appointed.exec"))

model.tc.base <- lm(turnout.coef ~ city_id_factor + presidential + xconst.lag + putin.app.3mo +  urgov + 
                  lnAvgSalary + dem + comp.scale2  + known.opp.mayor + appointed.exec + mayor.tenure, data = full.data)

stargazer::stargazer(model.tc.base, model.tc.tenure, type = "text", omit="city_id")
```

```{r}
model.ur.tenure <- lm(ur.voteshare ~ city_id_factor + presidential + xconst.lag + putin.app.3mo +  urgov + 
                  lnAvgSalary + dem + comp.scale2  + known.opp.mayor + appointed.exec*mayor.tenure + appointed.exec*mayor.tenure.sq + turnout.coef, data = full.data)

model.ur.base <- lm(ur.voteshare ~ city_id_factor + presidential + xconst.lag + putin.app.3mo +  urgov + 
                  lnAvgSalary + dem + comp.scale2  + known.opp.mayor + appointed.exec + mayor.tenure + turnout.coef, data = full.data)

stargazer::stargazer(model.ur.base, model.ur.tenure, type = "text", omit="city_id")

###All four models for appendix

stargazer::stargazer(model.tc.base, model.tc.tenure, model.ur.base, model.ur.tenure, type = "html", omit="city_id", out = "table_app_mayortenure.html")
```
###Plot of turnout coefs for main text

```{r}
novgorod <- read.csv("VelikijNovgorod2011.csv")
novgorod <- novgorod %>% mutate(region_name = "Velikij Novgorod")
volgodonsk <- read.csv("Volgodonsk2011.csv")
volgodonsk <- volgodonsk %>% mutate(region_name = "Volgodonsk")


combined.data <- bind_rows(novgorod, volgodonsk)

ggplot(combined.data, aes(x = turnout, y = ur.abshare)) +
  geom_point() +
  facet_wrap(~region_name) +
  geom_smooth(method = lm, se = FALSE) +
  xlab("Turnout") + ylab("UR absolute vote-share") +
  theme_bw()
```


##Looking at turnout coef across city size

```{r}
p.precincts <- ggplot(full.data, aes(x = n.precincts, y = turnout.coef, color = as.factor(appointed.exec))) +
  geom_point() + scale_color_grey("Appointed exec.") +
  geom_abline(slope = -0.00025, intercept = .763) +
  xlab("Number of precincts") +
  ylab("Estimated manipulation") +
  theme_bw()
```

##Thinking about unmanipulated support


###OLS

```{r}
model.ur2.nofe <- lm(ur.voteshare ~  urgov  + margin.most.recent + n.precincts + mayor.tenure +  lnAvgSalary + dem + comp.scale2 + known.opp.mayor +  years.under.regime + turnout.coef +
                      appointed.exec, data = full.data)


new.data <- model.ur2$model
new.data$turnout.coef <- 0


predicted.clean.support <- predict(model.ur2.nofe, newdata = new.data)

new.data2 <- cbind(new.data, predicted.clean.support)

summary(lm(predicted.clean.support ~ n.precincts, data = new.data2))

p.precincts.clean <- ggplot(new.data2, aes(x = n.precincts, y = predicted.clean.support)) +
  geom_point() + scale_color_grey("Appointed exec.") +
  geom_abline(intercept = .207, slope = -0.0000413) +
  xlab("Number of precincts") +
  ylab("Estimated clean support") +
  theme_bw()

```

##Thinking about models controlling for error in measurement

```{r}
model.ur.base <- lm(ur.voteshare ~  presidential + xconst.lag + putin.app.3mo  +  urgov  + margin.most.recent + n.precincts + mayor.tenure +  lnAvgSalary + dem + comp.scale2 + known.opp.mayor +  years.under.regime + turnout.coef +
                      appointed.exec, data = full.data, x = T)

model.ur.ethnic <- lm(ur.voteshare ~  presidential + xconst.lag + putin.app.3mo  +  urgov  + margin.most.recent + n.precincts + mayor.tenure +  lnAvgSalary + dem + comp.scale2 + known.opp.mayor +  years.under.regime + majority.russian.republic + majority.minority.republic + turnout.coef +
                      appointed.exec, data = full.data, x = T)

overall_sd_tc <- full.data %>% group_by(city_id) %>% summarise(sd_turnout = sd(turnout.coef))
summary(overall_sd_tc)

parl_sd_tc <- full.data %>% dplyr::filter(presidential == 0) %>% group_by(city_id) %>% summarise(sd_turnout = sd(turnout.coef))
summary(parl_sd_tc)

pres_sd_tc <- full.data %>% dplyr::filter(presidential == 1) %>% group_by(city_id) %>% summarise(sd_turnout = sd(turnout.coef))
summary(pres_sd_tc)

set.seed(3972)

model_simex <- simex(model.ur.base, SIMEXvariable = "turnout.coef", measurement.error = .2)
summary(model_simex)
print(summary(model_simex))
plot(model_simex)
plot(model_simex, show = c(rep(FALSE, 14), TRUE), ylab = c(rep("Blank", 14), "Appointed exec"))


model_simex_ethnic <- simex(model.ur.ethnic, SIMEXvariable = "turnout.coef", measurement.error = .2)
summary(model_simex_ethnic)
print(summary(model_simex_ethnic))
plot(model_simex_ethnic)
plot(model_simex_ethnic, show = c(rep(FALSE, 16), TRUE), ylab = c(rep("Blank", 16), "Appointed exec"))

texreg::htmlreg(list(model_simex, model_simex_ethnic), file = "./Output/simex_table.html")
```
## IPW with appointed.share

```{r}
##Note: including urvoteshare and/or turnoutcoef worsens balance on those variables, so they are excluded

covariates <- full.data %>% dplyr::select(city_id, presidential, xconst.lag, putin.app.3mo, urgov, mayor.tenure, lnAvgSalary, dem, comp.scale2, known.opp.mayor, margin.most.recent, year.x, treated.mod, turnout.coef, years.under.regime, ur.voteshare , treated.mod.1lag, treated.mod.2lag, treated.mod.3lag, years.with.elections, urvoteshare.1lag, turncoef.1lag, n.precincts, appointed.share.lag, appointed.share)
                                   
complete.tf <- complete.cases(covariates)
covariates <- bind_cols(covariates, complete.tf)
covariates <- covariates %>% dplyr::rename(complete.tf = ...26)

covariates <- covariates %>% filter(complete.tf == T)

data_long_sort <- covariates %>% dplyr::arrange(city_id, year.x)
data_long_sort <- data_long_sort %>% dplyr::select(-complete.tf)
data_long_sort <- data.frame(data_long_sort)

w <- ipwtm(
  exposure = treated.mod,
  family = "binomial",
  link = "logit",
  numerator = ~ treated.mod.1lag + treated.mod.2lag,
  denominator = ~ treated.mod.1lag + treated.mod.2lag + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent +  dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag + n.precincts + appointed.share.lag,
  id = city_id,
  timevar=year.x,
  type="first",
  data = data_long_sort)
summary(w$ipw.weights)
```

```{r}
iptw = w$ipw.weights


# Add the iptw variable onto a new dataframe = data2.
data2 <- cbind(data_long_sort, iptw)

##Truncated weights .95

data2 <- data2 %>% mutate(tsw = ifelse(iptw < quantile(iptw, probs=.05), quantile(iptw, probs=.05), iptw))

data2 <- data2 %>% mutate(tsw = ifelse(iptw > quantile(iptw, probs=.95), quantile(iptw, probs=.95), tsw))

summary(data2$tsw)
```
```{r}
###########################################################################################
# GEE model #2 - IPTW fitted to MSM with clustered robust SE
###########################################################################################
########################################################################
gee.iptw.tc <- geeglm(turnout.coef~ treated.mod + treated.mod.1lag + treated.mod.2lag + presidential + xconst.lag +
                     putin.app.3mo + 
                     mayor.tenure + appointed.share + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw.tc)
#m1 <- broom::tidy(gee.iptw)
#pixiedust::dust(m1) %>%
#  pixiedust::sprinkle_print_method("html")


gee.iptw2.vs <- geeglm(ur.voteshare~ treated.mod + treated.mod.1lag + treated.mod.2lag +  presidential + xconst.lag +
                      putin.app.3mo + mayor.tenure + appointed.share  + turnout.coef +  cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw2.vs)

#m2 <- broom::tidy(gee.iptw2)
#pixiedust::dust(m2) %>%
#  pixiedust::sprinkle_print_method("html")

sjPlot::tab_model(gee.iptw.tc, gee.iptw2.vs, show.ci = F, p.style = "stars", digits = 3, show.se = T, collapse.se =  T) #This is the model we want in the paper

```
