---
title: "R Notebook"
output: html_notebook
---

```{r setup}
library(readxl)
library(tidyverse)
library(CBPS)
library(lmtest)  #Getting clustered sEs 
library(sandwich)
library(ggplot2)
library(stargazer)
library(interplot)
#library(eventStudy)
library(data.table)
library(cobalt) #Balance; very useful package
library(broom)
library(fastDummies)
library(did) #Callaway and Sant'Anna
```


##Summary

Findings are variable by election type. Treatment appears to be variable by cohort and election type. Both treatment groups show higher levels of manipulation than control in the 2008 presidential election, even group 2 which has not yet been treated (anticipation?). In group 1, manipulation returns to control levels in 2012, and falls below control for gorup 2.  Treatment has a consistently positive significant effect for group 1 in the legislative elections of 2007 and 2011; there is no effect for either in group 2.

Note this looks at non-standard coef.

This looks to me like a descriptive Russia paper.

```{r}
full.data <- read.csv("coefs with city covariates cleaned.csv")
#absentee <- read.csv("absentee coefficients.csv")
#absentee <- absentee %>% dplyr::select(pct.absentee, city_id_year)
#full.data <- merge(full.data, absentee, by = "city_id_year")

#full.data <- read.csv("cleaned data full all years_v2.csv")

#full.data <- full.data %>% mutate(presidential = ifelse(year.x == 2003 | year.x == 2007 | year.x == 2011, 0, 1))

full.data <- full.data %>% mutate(years.since.treat = ifelse(is.na(cancel.year) == TRUE | cancel.year > year.x, 0, (year.x - cancel.year) + 1))

#full.data <- full.data %>% mutate(treat.weight.year = ifelse(treated.0708 == 1, treated.0708 / years.since.treat, 0))

full.data <- full.data %>% mutate(years_with_elections = ifelse(is.na(cancel.year) == TRUE, year.x - 2003, year.x - cancel.year))

##Replace NAs with 0 in cancel.year

full.data <- full.data %>% mutate(cancel.year = ifelse(is.na(cancel.year) == T, 0, cancel.year))


full.data <- full.data %>% mutate(election.period = ifelse(year.x == 2003, 1, ifelse(year.x == 2004, 2, ifelse(year.x
                                  == 2007, 3, ifelse(year.x == 2008, 4,
                                  ifelse(year.x == 2011, 5, 6))))))


#Codes abolitions in 2007 as part of wave 5 (keeping them as a separate group 4 results in a very small gorup). Same for abolitions in year 2011, now coded as occuring in period 5
full.data <- full.data %>% mutate(cancel.period = ifelse(cancel.year == 0, 0, ifelse(cancel.year == 2003, 1, ifelse(cancel.year >= 2004 & cancel.year <= 2007, 3, ifelse(
                                                   cancel.year >= 2008 & cancel.year <= 2011, 5, 6
                                                   )
                                                 )
)))

full.data <- full.data %>% mutate(years.since.treatment = ifelse(cancel.year == 0, 0, ifelse(year.x - cancel.year < 0, 0, year.x-cancel.year + 1)))

##Collapsed time periods

full.data <- full.data %>% mutate(election.period.small = ifelse(year.x == 2003 | year.x == 2004, 1, ifelse(year.x == 2007 | year.x == 2008, 2, 3)))

full.data <- full.data %>% mutate(cancel.period.small = ifelse(cancel.year == 0, 0, ifelse(cancel.year <= 2008, 2, 3)))

full.data <- full.data %>% mutate(cancel.period.f = as.factor(cancel.period))
full.data <- dummy_cols(full.data, select_columns = "cancel.period.f")

full.data <- full.data %>% rename(turnout.coef = turnout)

##Mod cancel.year to prevent post-treatment bias for 2008 and 2012
full.data <- full.data %>% mutate(cancel.year.mod = ifelse(is.na(cancel.year)==T, NA, ifelse(is.na(cancel.year)==F & cancel.year != 2008 & cancel.year != 2012, cancel.year, cancel.year + 1)))

##Known opp mayor
full.data <- full.data %>% mutate(known.opp.mayor = ifelse(is.na(opp_mayor1) == T, 0, ifelse(opp_mayor1==1, 1,0)))

##Years with eelections
full.data <- full.data %>% mutate(years.with.elections = ifelse(cancel.year == 0, year.x-1996, ifelse(year.x - cancel.year < 0, year.x - 1996, cancel.year - 1996)))
```


Data for presidential years only

```{r}
data.pres <- full.data %>% filter(year.x == 2004 | year.x == 2008 | year.x == 2012)
data.pres <- data.pres %>% mutate(cancel.period = ifelse(cancel.year == 0, 0, ifelse(cancel.year < 2004, 1, ifelse(cancel.year >= 2004 & cancel.year <= 2007, 2, 3
                                                   )
                                                 )
))
data.pres <- data.pres %>% mutate(election.period = ifelse(year.x == 2004, 1, ifelse(year.x == 2008, 2, 3)))

```


Data for legislative years only

```{r}
data.parl <- full.data %>% filter(year.x == 2003 | year.x == 2007 | year.x == 2011)
data.parl <- data.parl %>% mutate(cancel.period = ifelse(cancel.year == 0, 0, ifelse(cancel.year < 2003, 1, ifelse(cancel.year >= 2004 & cancel.year < 2007, 2, 3
                                                   )
                                                 )
))
data.parl <- data.parl %>% mutate(election.period = ifelse(year.x == 2003, 1, ifelse(year.x == 2007, 2, 3)))

```


##Between group comps

```{r}
ggstatsplot::ggbetweenstats(
  data = full.data %>% filter(year.x == 2004),
  x = cancel.period.f,
  y = ur.voteshare,
  title = "UR voteshare (pres)"
)

ggstatsplot::ggbetweenstats(
  data = full.data %>% filter(year.x == 2003),
  x = cancel.period.f,
  y = ur.voteshare,
  title = "UR voteshare (parl)"
)
```


```{r}
ggstatsplot::ggbetweenstats(
  data = full.data %>% filter(year.x == 2004),
  x = cancel.period.f,
  y = turnout.coef,
  title = "Turnout coef (pres)"
)

ggstatsplot::ggbetweenstats(
  data = full.data %>% filter(year.x == 2003),
  x = cancel.period.f,
  y = turnout.coef,
  title = "Turnout coef (parl)"
)
```

```{r}
ggstatsplot::ggbetweenstats(
  data = full.data %>% filter(year.x == 2004),
  x = cancel.period.f,
  y = margin,
  title = "Mayor margins"
)

ggstatsplot::ggbetweenstats(
  data = full.data %>% filter(year.x == 2004),
  x = cancel.period.f,
  y = dem,
  title = "Dem score"
)
```



##Correlations

```{r}
ggstatsplot::ggcorrmat(
  data = full.data,
  type = "robust", # correlation method
  cor.vars = c(cancel.period.f_0, cancel.period.f_3, cancel.period.f_5, lag.manipulation, dem, margin, urgov, lnAvgSalary, kprf99), # a range of variables can be selected
  cor.vars.names = c(
    "Control", # variable names
    "Early cohort",
    "Late cohort",
    "Lag manip.",
    "Dem score",
    "Mayor margin",
    "UR gov.",
    "Log avg. salary",
    "KPRF-99"
  ),
  colors = c("#B2182B", "white", "#4D4D4D"),
  title = "Correlalogram ",
  caption = "Source: `ggplot2` R package"
)
```
Takeaway: The late cohort is likely to be more democratic, to have weaker mayoral machines, and to be worse at manipulation. Thus we see a weaker effect in that group for manipulation after takeover. Strongest mayors are in the control group.

##Pre-test

```{r}
cdp <- conditional_did_pretest("turnout.coef", "election.period", "city_id", "cancel.period", xformla=~margin_pretreat_final, data=full.data %>% filter(is.na(margin_pretreat_final) == F))
summary(cdp)
```

##Model
Note the model can only take time-invariant covariates, and will coerce non-constant covariates to that of the unit's first observation by time

Also exclude transitions that eliminate an opposition mayor

###Presidential--overall
```{r}
data.complete <- data.pres %>%  dplyr::select(turnout.coef, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "turnout.coef",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

###Presidential--nonstandard
```{r}
data.complete <- data.pres %>%  dplyr::select(nonstandard.coef, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "nonstandard.coef",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

###Presidential--absentee
```{r}
data.complete <- data.pres %>%  dplyr::select(pct.absentee, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "pct.absentee",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

###Presidential--UR vote
```{r}
data.complete <- data.pres %>%  dplyr::select(ur.voteshare, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "ur.voteshare",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

##Parliamentary--overall

```{r}
data.complete <- data.parl %>% dplyr::select(turnout.coef, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "turnout.coef",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = "city_id",
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```


##Parliamentary--nonstandard

```{r}
data.complete <- data.parl %>% dplyr::select(nonstandard.coef, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "nonstandard.coef",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = "city_id",
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

##Parliamentary--absentee

```{r}
data.complete <- data.parl %>% dplyr::select(pct.absentee, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "pct.absentee",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = "city_id",
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```


##Parliamentary--UR

```{r}
data.complete <- data.parl %>% dplyr::select(ur.voteshare, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "ur.voteshare",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = "city_id",
              bstrap = T,
              cband = T)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

##All--overall
Note: the group-time estimates will work with year.x and cancel.year, but not the other elements.

I think the inability to control for time-variant covariates makes this a not-useful approach.
```{r}
data.complete <- full.data %>%  dplyr::select(turnout.coef, cancel.year.mod, city_id, year.x, ethnic.categorical) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "turnout.coef",
              gname = "cancel.year.mod",
              idname = "city_id",
              tname = "year.x",
              xformla = ~ as.factor(ethnic.categorical),
              data = data.complete,
              est_method = "dr",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T,
              allow_unbalanced_panel = F)#,
              #anticipation = 1)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```


##All -- nonstandard

```{r}
data.complete <- full.data %>%  dplyr::select(nonstandard.coef, cancel.year, city_id, year.x, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "nonstandard.coef",
              gname = "cancel.year",
              idname = "city_id",
              tname = "year.x",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T,
              anticipation = 1)#,
              #anticipation = 1)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

##All--UR voteshare
```{r}
data.complete <- full.data %>%  dplyr::select(ur.voteshare, cancel.year, city_id, year.x, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "ur.voteshare",
              gname = "cancel.year",
              idname = "city_id",
              tname = "year.x",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T,
              anticipation = 1)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```


##All--absentee coefficient
```{r}
data.complete <- full.data %>%  dplyr::select(pct.absentee, cancel.period, city_id, election.period, 
                                 dem) %>% filter(city_id != 90)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "pct.absentee",
              gname = "cancel.period",
              idname = "city_id",
              tname = "election.period",
              xformla = ~ dem,
              data = data.complete,
              est_method = "reg",
              clustervars = c("city_id"),
              bstrap = T,
              cband = T,
              anticipation = 1)
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

simp <- aggte(out, type = "simple")
summary(simp)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

##Model for collapsed periods

Must divide out by presidential and legislative elections

Legislative elections   
```{r}
data.complete <- full.data %>% filter(year.x == 2003 | year.x == 2007 | year.x == 2011) %>% dplyr::select(turnout.coef, cancel.period.small, city_id, election.period.small, 
                                 lnAvgSalary, poppopprop, ethnic.categorical, year.x)
data.complete <- data.complete[complete.cases(data.complete),]

out <- att_gt(yname = "turnout.coef",
              gname = "cancel.period.small",
              idname = "city_id",
              tname = "election.period.small",
              xformla = ~ lnAvgSalary + poppopprop + ethnic.categorical,
              data = data.complete,
              est_method = "reg",
              clustervars = "city_id",
              bstrap = T,
              cband = T
              )
summary(out)
ggdid(out)

es <- aggte(out, type = "dynamic")
summary(es)
ggdid(es)

group_effects <- aggte(out, type = "group")
summary(group_effects)
```

