---
title: "Event study models"
output: html_notebook
---

##Summary

Findings are variable by election type. Treatment appears to reduce manipulation levels for presidential elections. This is consistent across Callaway and Sant'Anna models and standard dynamic models included on this page, when presidential and legislative elections are modeled separately (for consistency with C&S models, which require this). C&S models break out effects for cohorts, and show that the effect for legislative elections is driven by the early cohort. For presidential elections the effect is seen in both cohorts, but is strongest in the later cohort.


##Setup

```{r setup}
library(readxl)
library(tidyverse)
library(CBPS)
library(lmtest)  #Getting clustered sEs 
library(sandwich)
library(ggplot2)
library(stargazer)
library(interplot)
library(fastDummies)
library(eventStudy)
library(data.table)
library(ggeffects)
library(cobalt) #Balance; very useful package
```

##Data

```{r}
full.data <- read.csv("cleaned data full all years_v2.csv")

full.data <- full.data %>% mutate(presidential = ifelse(year.x == 2004 | year.x == 2008 | year.x == 2012, 1, 0))

full.data <- full.data %>% mutate(years.since.treat = ifelse(is.na(cancel.year) == TRUE | cancel.year > year.x, 0, (year.x - cancel.year) + 1))

#full.data <- full.data %>% mutate(treat.weight.year = ifelse(treated.0708 == 1, treated.0708 / years.since.treat, 0))

full.data <- full.data %>% mutate(years_with_elections = ifelse(is.na(cancel.year) == TRUE, year.x - 2003, year.x - cancel.year))

full.data <- full.data %>% mutate(turnout.coef.susp = ifelse(turnout.coef >= 1, 1, 0))


full.data <- full.data %>% mutate(election.period = ifelse(year.x == 2003, 1, ifelse(year.x == 2004, 2, ifelse(year.x
                                  == 2007, 3, ifelse(year.x == 2008, 4,
                                  ifelse(year.x == 2011, 5, 6))))))

full.data <- full.data %>% mutate(treat.cohort = ifelse(is.na(cancel.year) == TRUE, "Inf", ifelse(cancel.year >= 2004 &                                                  cancel.year < 2007, 2, ifelse(
                                                 cancel.year == 2007, 3, ifelse(
                                                   cancel.year >= 2008 & cancel.year < 2011, 4, ifelse(
                                                     cancel.year == 2011, 5, "Inf"
                                                   )
                                                 )
))))



#full.data <- full.data %>% mutate(rel.treat.time = ifelse(treat.cohort == "Inf", 0, time.period - as.numeric(treat.cohort)))

full.data <- full.data %>% mutate(treat.cohort = factor(treat.cohort))

#Next make individual variables for each level of the factor; also try the same approach with only three periods (year <= 2004 = 0, year <=2008 = 1, year <= 2012 = 2)




full.data <- full.data %>% mutate(cohort2 = ifelse(as.numeric(treat.cohort) == 2, 1, 0))
full.data <- full.data %>% mutate(cohort3 = ifelse(as.numeric(treat.cohort) == 3, 1, 0))
full.data <- full.data %>% mutate(cohort4 = ifelse(as.numeric(treat.cohort) == 4, 1, 0))
full.data <- full.data %>% mutate(cohort5 = ifelse(as.numeric(treat.cohort) == 5, 1, 0))
full.data <- full.data %>% mutate(cohort_inf = ifelse(treat.cohort == "Inf", 1, 0))

full.data <- full.data %>% mutate(appointed.exec = ifelse(treated.0708 == 1 | treated.1112, 1, 0))
#full.data <- full.data %>% mutate(appointed.exec = ifelse(year.x == 2003, NA, appointed.exec))

full.data <- full.data %>% mutate(elected.transition = ifelse(year.x < cancel.year & exec.first.election == 1, 1, 0))
full.data <- full.data %>% mutate(appointed.transition = ifelse(year.x >= cancel.year & cross.regime.transition == 0 & exec.first.election == 1, 1, 0))


full.data <- 
    full.data %>%
    group_by(city_id) %>%
    mutate(lag.manipulation = dplyr::lag(turnout.coef, n = 1, default = NA)) #Lagging manipulation

full.data <- full.data %>% mutate(known.opp.mayor = ifelse(opp_mayor1 == 1, 1, 0))
```

Creating relative treatment counter using time.period instead of calendar time
Time periods are:
2003 == 1
2004 == 2
2007 == 3
2008 == 4
2011 == 5
2012 == 6

Treatment period should collapse to the previous election time. I.e. elections canceled between 2004 and 2007 should score as 2, so that they are 1 period post treatment by 2007 election

```{r}
full.data <- full.data %>% mutate(cancel.period = ifelse(is.na(cancel.year) == TRUE, NA, ifelse(
  cancel.year < 2007, 3, ifelse(
    cancel.year == 2007, 5, ifelse(
      cancel.year > 2007 & cancel.year <= 2011, 5, ifelse(
        cancel.year == 2011, 6, NA
      )
    ) 
  )
)))

#full.data <- full.data %>% mutate(rel.treat.period = ifelse())
```

```{r}
full.data <- full.data %>% mutate(election.period = as.integer(election.period))
full.data <- full.data %>% mutate(cancel.period = as.integer(cancel.period))

full.data.table <- data.table(full.data)

full.data <- full.data %>% mutate(rel.treat.time = ifelse(is.na(cancel.period) == TRUE, -1, election.period - cancel.period))


full.data <- full.data %>%
  mutate(rel.treat.time2 = rel.treat.time)

full.data <- full.data %>%
  mutate(value = 1,
         rel.treat.time2 = paste0("rel.time", rel.treat.time2)) %>%
  spread(rel.treat.time2, value, fill = 0)


full.data <- full.data %>% mutate(cohort1 = ifelse(cancel.period == 1, 1, 0))
full.data <- full.data %>% mutate(cohort2 = ifelse(cancel.period == 2, 1, 0))
full.data <- full.data %>% mutate(cohort3 = ifelse(cancel.period == 3, 1, 0))
full.data <- full.data %>% mutate(cohort4 = ifelse(cancel.period == 4, 1, 0))
full.data <- full.data %>% mutate(cohort5 = ifelse(cancel.period == 5, 1, 0))
full.data <- full.data %>% mutate(cohort6 = ifelse(cancel.period == 6, 1, 0))
full.data <- full.data %>% mutate(cohort.untreat = ifelse(is.na(cancel.period) == T, 1, 0))


full.data <- full.data %>%
  mutate(ethnic.categorical2 = ethnic.categorical)

full.data <- full.data %>%
  mutate(value = 1,
         ethnic.categorical2 = paste0("ethcat", ethnic.categorical2)) %>%
  spread(ethnic.categorical2, value, fill = 0)


##Years before and after treatment

full.data <- full.data %>% mutate(years.after.treatment.factor = ifelse(is.na(cancel.year)==T, -1, year.x - cancel.year))
#full.data <- dummy_cols(full.data, select_columns = "years.after.treatment.factor")
```


Looking at balance; there isn't much difference on any of these dimensions except 'dem'.

```{r}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


##Testing balance

```{r}
###Untreated vs. early treated
treated.obs1 <- full.data %>% filter(year.x <= 2008) %>% data.frame()
covs <- treated.obs1  %>% dplyr::select(nonstandard.coefs03, ur.coef.2003, ur.voteshare.2003,
                             nonstandard.coefs04, ur.coef.2004, ur.voteshare.2004, dem, civsoc91,
                             kprf99, education, pctRussian2002_new, opp_mayor1, lag.manipulation) %>% data.frame()
bal.tab(covs, treat = treated.obs1$treated.0708)
p.bal.ns03 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "nonstandard.coefs03")
p.bal.ns04 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "nonstandard.coefs04")
p.bal.urc03 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.coef.2003") + labs(title = "", x = "United Russia manipulation coefficient\n (2003)")
p.bal.urc04 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.coef.2004") +  labs(title = "", x = "United Russia manipulation coefficient\n (2004)")
p.bal.urvs03 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.voteshare.2003") + labs(title = "", x = "United Russia vote-share\n (2003)")
p.bal.urvs04 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.voteshare.2004") + labs(title = "", x = "United Russia vote-share\n (2004)")
p.bal.dem <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "dem")
p.bal.rus <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "pctRussian2002_new")
p.bal.opp <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "opp_mayor1") + labs(title = "Distributional Balance for 'opposition mayor', first wave", x = "Opposition mayor")
p.bal.lagman <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "lag.manipulation") + labs(title = "Distributional Balance for 'opposition mayor', first wave", x = "Lagged manipulation")

full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.coef.2003, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.coef.2004, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.voteshare.2003, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.voteshare.2004, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(dem, na.rm=TRUE))

###Early treated vs late treated
treated.obs2 <- full.data %>% filter(year.x >= 2007 & treated.0708 == 0 | treated.1112 == 1)
covs <- treated.obs2  %>% dplyr::select(nonstandard.coefs03, ur.coef.2003, ur.voteshare.2003,
                             nonstandard.coefs04, ur.coef.2004, ur.voteshare.2004, ur.coef.2007, ur.voteshare.2007, ur.coef.2008, ur.voteshare.2008,  dem, civsoc91,
                             kprf99, education, pctRussian2002_new, opp_mayor1, lag.manipulation) %>% data.frame()
bal.tab(covs, treat = treated.obs2$treated.1112)
p.bal.ns03.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "nonstandard.coefs03")
p.bal.ns04.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "nonstandard.coefs04")
p.bal.urc03.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2003")
p.bal.urc04.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2004")
p.bal.urvs03.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2003")
p.bal.urvs04.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2004")
p.bal.urc07.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2007")
p.bal.urvs07.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2007")
p.bal.urc08.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2008")
p.bal.urvs08.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2008")
p.bal.dem.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "dem")
p.bal.rus.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "pctRussian2002_new")
p.bal.opp2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "opp_mayor1") + labs(title = "Distributional Balance for 'opposition mayor'", x = "Opposition mayor")
p.bal.lagman2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "lag.manipulation") + labs(title = "Distributional Balance for 'opposition mayor', first wave", x = "Lagged manipulation")


treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.coef.2007, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.coef.2008, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.voteshare.2007, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.voteshare.2008, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(dem, na.rm=TRUE))

###Multiplotting
multiplot(p.bal.urc03, p.bal.urc04, p.bal.urvs03, p.bal.urvs04, cols= 2)

multiplot(p.bal.urc07.2, p.bal.urc08.2, p.bal.urvs07.2, p.bal.urvs08.2, cols= 2)


```


##Presidential vs legislative data

```{r}
data.pres <- full.data %>% filter(presidential == 1)
data.pres <- data.pres %>% mutate(election.period = ifelse(year.x == 2004, 1, ifelse(year.x == 2008, 2, 3)))
data.pres <- data.pres %>%  mutate(cancel.period = ifelse(is.na(cancel.year) == TRUE, NA, ifelse(
  cancel.year <= 2007, 2, 3)))
data.pres <- data.pres %>% mutate(rel.treat.time = ifelse(is.na(cancel.period) == T, -1, election.period - cancel.period))
data.pres <- dummy_cols(data.pres, select_columns = "rel.treat.time")
```


```{r}
data.parl <- full.data %>% filter(presidential == 0)
data.parl <- data.parl %>% mutate(election.period = ifelse(year.x == 2003, 1, ifelse(year.x == 2007, 2, 3)))
data.parl <- data.parl %>%  mutate(cancel.period = ifelse(is.na(cancel.year) == TRUE, NA, ifelse(
  cancel.year < 2007, 2, 3)))
data.parl <- data.parl %>% mutate(rel.treat.time = ifelse(is.na(cancel.period) == T, -1, election.period - cancel.period))
data.parl <- dummy_cols(data.parl, select_columns = "rel.treat.time")
```

##Models

###Baseline models

```{r}
model.tc.dyn <- lm(turnout.coef ~ factor(city_id) + presidential + years.since.treatment + I(years.since.treatment^2) 
                   + urgov + mayor.tenure + lnAvgSalary, data = test)
summary(model.tc.dyn)

dat <- ggpredict(model.tc.dyn, terms = "years.since.treatment")

ggplot(dat, aes(x, predicted)) + 
  geom_line() +
  geom_point() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)
```


Manipulation overall

```{r}
model.tc.dyn.parl <- lm(nonstandard.coef ~ factor(city_id) + factor(year.x) + `rel.treat.time_-2` +  
                        `rel.treat.time_0` + rel.treat.time_1 
                   + urgov + years.since.treatment + mayor.tenure + lnAvgSalary + dem, data = data.parl)
summary(model.tc.dyn.parl)
```

```{r}
model.tc.dyn.pres <- lm(nonstandard.coef ~ factor(city_id) + factor(year.x) + `rel.treat.time_-2` +  
                        `rel.treat.time_0` + rel.treat.time_1 
                   + urgov + years.since.treatment + mayor.tenure + lnAvgSalary + dem, data = data.pres)
summary(model.tc.dyn.pres)

```


```{r}
model.tc.dyn.all <- lm(nonstandard.coef ~ factor(city_id) + presidential + `rel.time-4` + `rel.time-3` + `rel.time-2` +  
                        `rel.time0` + rel.time1 + rel.time2 + rel.time3
                   + urgov + years.since.treatment + mayor.tenure  + lnAvgSalary + dem, data = full.data)
summary(model.tc.dyn.all)

```

###UR voteshare



```{r}
model.ur.dyn.parl <- lm(ur.voteshare ~ factor(city_id) + factor(year.x) + `rel.treat.time_-2` +  
                        `rel.treat.time_0` + rel.treat.time_1 
                   + urgov + years.since.treatment + mayor.tenure + lnAvgSalary + dem + turnout.coef, data = data.parl)
summary(model.ur.dyn.parl)

```


```{r}
model.ur.dyn.pres <- lm(ur.voteshare ~ factor(city_id) + factor(year.x) + `rel.treat.time_-2` +  
                        `rel.treat.time_0` + rel.treat.time_1 
                   + urgov + years.since.treatment + mayor.tenure + lnAvgSalary + dem + turnout.coef, data = data.pres)
summary(model.ur.dyn.pres)

```

```{r}
model.ur.dyn.all <- lm(ur.voteshare ~ factor(city_id) + presidential + `rel.time-4` + `rel.time-3` + `rel.time-2` +  
                        `rel.time0` + rel.time1 + rel.time2 + rel.time3
                   + urgov + years.since.treatment + mayor.tenure + lnAvgSalary + dem + turnout.coef, data = full.data)
summary(model.ur.dyn.all)

```


Manipulation plot
```{r}
coefs.homog <- broom::tidy(model.tc.dyn.all, conf.int = TRUE, conf.level = .95)
coefs.homog.select <- coefs.homog[131:137,]
coefs.homog.select <- coefs.homog.select %>% mutate(rel.time = c(-4, -3, -2, -1, 1, 2, 3))
new.row <- c(rep(NA, 6), 0)
coefs.homog.select <- rbind(coefs.homog.select, new.row)

att.plot.tc <- ggplot(coefs.homog.select, aes(x = rel.time, y = estimate)) + geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + labs(title = "OLS estimates of relative time to treatment\n (95% confidence intervals)", x = "Time to treatment", y = "Estimate") + theme_bw()

```

Vote-share plot
```{r}
coefs.homog <- broom::tidy(model.ur.dyn, conf.int = TRUE, conf.level = .95)
coefs.homog.select <- coefs.homog[131:137,]
coefs.homog.select <- coefs.homog.select %>% mutate(rel.time = c(-4, -3, -2, -1, 1, 2, 3))
new.row <- c(rep(NA, 6), 0)
coefs.homog.select <- rbind(coefs.homog.select, new.row)

att.plot.ur <- ggplot(coefs.homog.select, aes(x = rel.time, y = estimate)) + geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + labs(title = "OLS estimates of relative time to treatment\n (95% confidence intervals)", x = "Time to treatment", y = "Estimate") + theme_bw()

```

###With lagged manipulation

Manipulation overall
```{r}
model.tc.dyn2 <- lm(turnout.coef ~ factor(city_id) + factor(year.x)  +  `rel.time-4` +
                        `rel.time-3` + `rel.time-2` + `rel.time-1` + rel.time1 + rel.time2 + rel.time3 
                   + urgov + mayor.tenure + lag.manipulation, data = full.data)
summary(model.tc.dyn2)
```

UR voteshare
```{r}
model.ur.dyn2 <- lm(ur.voteshare ~ factor(city_id) + factor(year.x) + `rel.time-4` +
                        `rel.time-3` + `rel.time-2` + `rel.time-1` + rel.time1 + rel.time2 + rel.time3 
                   + urgov + mayor.tenure + turnout.coef + lag.manipulation, data = full.data)
summary(model.ur.dyn2)
```
