---
title: "R Notebook"
output: html_notebook
---

Apparently there is an issue with eventStudy overwriting some data, so it is wise to re-set the dataframe before each model.


Note also, UR models are not helpful since they do not control for turnout.coef.

Next step is to add residualize_coarviates to the ES step, adding necessary control variables.
```{r setup}
library(tidyverse)
library(interactions)
library(ggplot2)
library(stargazer)
library(eventStudy)
library(fastDummies)

full.data <- read.csv("coefs with city covariates cleaned.csv")
```

EventStudy package links here: https://github.com/setzler/eventStudy 

##Data transformations


```{r}
full.data <- full.data %>% mutate(presidential = ifelse(year.x == 2004 | year.x == 2008 | year.x == 2012, 1, 0))
full.data <- full.data %>% mutate(known.opp.mayor = ifelse(is.na(opp_mayor1) == T, 0, ifelse(opp_mayor1==1, 1,0)))
full.data <- full.data %>% rename(turnout.coef = turnout)

##Year and country factors

full.data <- full.data %>% mutate(city_id_factor = as.factor(city_id))
full.data <- full.data %>% mutate(year_factor = as.factor(year.x))

##Explanatory variables for OLS
full.data <- full.data %>% mutate(appointed.exec = ifelse(is.na(cancel.year)==T, 0, ifelse(year.x >= cancel.year, 1, 0)))
full.data <- full.data %>% mutate(years.under.regime = ifelse(appointed.exec == 0, year.x - 2000, year.x - cancel.year))

full.data <- full.data %>% mutate(years.with.elections = ifelse(is.na(cancel.year)==T, year.x-1996, ifelse(year.x - cancel.year < 0, year.x - 1996, cancel.year - 1996))) #This gives a measure of early vs late vs. control; 1996 bc this is when local elections first took place 


##Adjusting treatment year to push treatments in 2008 and 2012 to the next year (so they do not affect elections in those years)

full.data <- full.data %>% mutate(cancel.year.adj = ifelse(cancel.year == 2004, 2005,
                                                    ifelse(cancel.year == 2008, 2009, 
                                                    ifelse(cancel.year == 2012, NA, cancel.year))))
full.data <- full.data %>% mutate(cancel.year.adj = as.integer(cancel.year.adj))

##Dummies for ethnic categorical

full.data <- dummy_cols(full.data, select_columns = "ethnic.categorical")
full.data <- full.data %>% rename(majority.russian.republic = ethnic.categorical_Majority_Russian_republic)
full.data <- full.data %>% rename(majority.minority.republic = `ethnic.categorical_Majority-minority_republic`)

##Known opp mayor
full.data <- full.data %>% mutate(known.opp.mayor = ifelse(is.na(opp_mayor1) == T, 0, ifelse(opp_mayor1==1, 1,0)))

```

Separate into pres and parl

```{r}
pres.data <- full.data %>% filter(presidential == 1)
parl.data <- full.data %>% filter(presidential == 0)
```


##Estimation: all data

Overall

```{r}
##Convert to data.table
full.data2 <- full.data %>% filter(is.na(urgov)==F) %>% data.table::data.table()
results <- ES(long_data=full.data2, outcomevar="turnout.coef", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2,
              residualize_covariates = T,
              #anticipation = 1,
              discrete_covars = c("urgov", "known.opp.mayor", "majority.russian.republic", "majority.minority.republic"),
              cont_covars = c("margin.most.recent", "lnAvgSalary", "poppopprop", "civsoc91", "mayor.tenure", "education", "unemployrate"))
p.tc.means <- ES_plot_levels(results, lower_event = -7, upper_event = 9) + ylab("Mean of the Outcome") + facet_wrap(vars(ref_onset_time))
p.tc.means
p.tc.hetero <- ES_plot_ATTs(results, lower_event = -7, upper_event = 9) + ylab("ATT Estimate (95% CI)")
p.tc.hetero
p.tc.homo <- ES_plot_ATTs(results, lower_event = -7, upper_event = 9, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")
p.tc.homo

png(filename = "turnout coefficient cohort means.png", width = 7, height = 5, units = "in",
    res = 500)
p.tc.means
dev.off()

png(filename = "turnout coefficient heterogenous att.png", width = 7, height = 5, units = "in",
    res = 500)
p.tc.hetero
dev.off()
```


Nonstandard


```{r}
full.data2 <- full.data %>% filter(is.na(urgov)==F) %>% data.table::data.table()
results <- ES(long_data=full.data2, outcomevar="nonstandard.coef", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2,
              residualize_covariates = T,
              discrete_covars = c("presidential", "urgov"),
              cont_covars = c("margin.most.recent", "lnAvgSalary", "poppopprop", "civsoc91", "mayor.tenure", "education", "unemployrate", "majority.russian.republic", "majority.minority.republic"))
ES_plot_levels(results, lower_event = -7, upper_event = 7) + ylab("Mean of the Outcome") + facet_wrap(vars(ref_onset_time))
ES_plot_ATTs(results, lower_event = -7, upper_event = 7) + ylab("ATT Estimate (95% CI)")
ES_plot_ATTs(results, lower_event = -7, upper_event = 7, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")
```


UR voteshare


```{r}
##Convert to data.table
full.data2 <- full.data %>% filter(is.na(urgov)==F) %>% data.table::data.table()
results <- ES(long_data=full.data2, outcomevar="ur.voteshare", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2,
              residualize_covariates = T,
              #anticipation = 1,
              discrete_covars = c("urgov", "known.opp.mayor", "majority.russian.republic", "majority.minority.republic"),
              cont_covars = c("margin.most.recent", "lnAvgSalary", "poppopprop", "civsoc91", "mayor.tenure", "education", "unemployrate", "turnout.coef"))
p.ur.means <- ES_plot_levels(results, lower_event = -7, upper_event = 9) + ylab("Mean of the Outcome") + facet_wrap(vars(ref_onset_time))
p.ur.means
p.ur.hetero <- ES_plot_ATTs(results, lower_event = -7, upper_event = 9) + ylab("ATT Estimate (95% CI)")
p.ur.hetero
p.ur.homo <- ES_plot_ATTs(results, lower_event = -7, upper_event = 9, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")
p.ur.homo

png(filename = "voteshare cohort means.png", width = 7, height = 5, units = "in",
    res = 500)
p.ur.means
dev.off()

png(filename = "voteshare heterogenous att.png", width = 7, height = 5, units = "in",
    res = 500)
p.ur.hetero
dev.off()
```


##Estimation: pres data

```{r}
pres2 <- data.table::data.table(pres.data)
results <- ES(long_data=pres2, outcomevar="turnout.coef", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2)
ES_plot_levels(results, lower_event = -8, upper_event = 8) + ylab("Mean of the Outcome")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8) + ylab("ATT Estimate (95% CI)")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")

```


```{r}
pres2 <- data.table::data.table(pres.data)
results <- ES(long_data=pres2, outcomevar="nonstandard.coef", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2)
ES_plot_levels(results, lower_event = -8, upper_event = 8) + ylab("Mean of the Outcome")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8) + ylab("ATT Estimate (95% CI)")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")

```

```{r}
pres2 <- data.table::data.table(pres.data)
results <- ES(long_data=pres2, outcomevar="ur.voteshare", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2)
ES_plot_levels(results, lower_event = -8, upper_event = 8) + ylab("Mean of the Outcome")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8) + ylab("ATT Estimate (95% CI)")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")

```


###Parl

```{r}
parl2 <- data.table::data.table(parl.data)
results <- ES(long_data=parl2, outcomevar="turnout.coef", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2)
ES_plot_levels(results, lower_event = -8, upper_event = 8) + ylab("Mean of the Outcome")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8) + ylab("ATT Estimate (95% CI)")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")

```


```{r}
parl2 <- data.table::data.table(parl.data)
results <- ES(long_data=parl2, outcomevar="nonstandard.coef", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2)
ES_plot_levels(results, lower_event = -8, upper_event = 8) + ylab("Mean of the Outcome")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8) + ylab("ATT Estimate (95% CI)")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")

```

```{r}
parl2 <- data.table::data.table(parl.data)
results <- ES(long_data=parl2, outcomevar="ur.voteshare", 
              unit_var="city_id", cal_time_var="year.x", 
              onset_time_var="cancel.year.adj", cluster_vars="city_id",
              never_treat_action = "only",  #uses never-treated as controls; set to "keep" to use never-treated and not-yet treated as controls
              omitted_event_time = -2)
ES_plot_levels(results, lower_event = -8, upper_event = 8) + ylab("Mean of the Outcome")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8) + ylab("ATT Estimate (95% CI)")
ES_plot_ATTs(results, lower_event = -8, upper_event = 8, homogeneous_ATT = T) + ylab("ATT Estimate (95% CI)")

```
