---
title: "Inverse probability weighting and marginal structural models"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(interactions)
library(stargazer)
library(fastDummies)
library(geepack)
library(survey)
library(ipw)
library(reshape)
#full.data <- read.csv("cleaned data full all years_v2.csv")

full.data <- read.csv("coefs with city covariates cleaned.csv")
#absentee <- read.csv("absentee coefficients.csv")
#absentee <- absentee %>% dplyr::select(pct.absentee, city_id_year)
#full.data <- merge(full.data, absentee, by = "city_id_year")

#Note: Missing cities are manually added to full.data file

full.data <- full.data %>% mutate(presidential = ifelse(year.x == 2004 | year.x == 2008 | year.x == 2012, 1, 0))
full.data <- full.data %>% mutate(known.opp.mayor = ifelse(is.na(opp_mayor1) == T, 0, ifelse(opp_mayor1==1, 1,0)))
full.data <- full.data %>% mutate(appointed.exec = ifelse(is.na(cancel.year)==T, 0, ifelse(year.x >= cancel.year, 1, 0)))
full.data <- full.data %>% dplyr::rename(turnout.coef = turnout)

full.data <- full.data %>% mutate(years.with.elections = ifelse(is.na(cancel.year)==T, year.x-1996, ifelse(year.x - cancel.year < 0, year.x - 1996, cancel.year - 1996))) #This gives a measure of early vs late vs. control; 1996 bc this is when local elections first took place 

full.data <- full.data %>% mutate(years.post.treatment = ifelse(is.na(cancel.year)==T, 0, ifelse(year.x - cancel.year < 0, 0, year.x - cancel.year)))
full.data <- full.data %>% mutate(years.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2007 & year.x ==2007, 1, years.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.
full.data <- full.data %>% mutate(years.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2011 & year.x ==2011, 1, years.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.

full.data <- full.data %>% mutate(treated.post.treatment = ifelse(is.na(cancel.year)==T, 0, ifelse(year.x - cancel.year < 0, 0, 1)))
full.data <- full.data %>% mutate(treated.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2007 & year.x ==2007, 1, treated.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.
full.data <- full.data %>% mutate(treated.post.treatment = ifelse(is.na(cancel.year)==F & cancel.year == 2011 & year.x ==2011, 1, treated.post.treatment)) #This codes cancelations in 2007 and 2011 as 1 for those years, since elections take place at year-end.


full.data <- full.data %>% mutate(years.under.appt = ifelse(is.na(cancel.year) == T, 0, ifelse(year.x - cancel.year < 0, 0, ifelse(year.x == 2007 | year.x == 2011 & year.x == cancel.year, 1, year.x - cancel.year))))

full.data <- full.data %>% mutate(city_id_factor = as.factor(city_id))


full.data <- full.data %>% mutate(treatment.group = ifelse(is.na(cancel.year)==F, 1, 0))

full.data <- full.data %>% mutate(control = ifelse(is.na(cancel.year)==T, 1, 0))
full.data <- full.data %>% mutate(early.treated = ifelse(is.na(cancel.year)==F & cancel.year <= 2007, 1, 0))
full.data <- full.data %>% mutate(late.treated = ifelse(is.na(cancel.year)==F & cancel.year > 2007, 1, 0))


full.data <- full.data %>% mutate(years.under.regime = ifelse(appointed.exec == 0, year.x - 2000, year.x - cancel.year))

##Dummies for ethnic categorical

full.data <- dummy_cols(full.data, select_columns = "ethnic.categorical")
full.data <- full.data %>% dplyr::rename(majority.russian.republic = ethnic.categorical_Majority_Russian_republic)
full.data <- full.data %>% dplyr::rename(majority.minority.republic = `ethnic.categorical_Majority-minority_republic`)

##Lagged treatments
###Note: go into earlier data frame and lag by year, not by period

full.data <- full.data %>% mutate(cancel.year.mod = ifelse(is.na(cancel.year)==T, NA, ifelse(is.na(cancel.year)==F & cancel.year != 2008 & cancel.year != 2012, cancel.year, cancel.year + 1)))

full.data <- full.data %>% mutate(treated.mod = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.1lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 1, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.2lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 2, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.3lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 3, 1, 0)))

full.data <- full.data %>% mutate(treated.mod.4lag = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(year.x >= cancel.year.mod + 4, 1, 0)))


##Lagged DVs

full.data <- full.data %>% group_by(city_id) %>% mutate(turncoef.1lag = lag(turnout.coef))
full.data <- full.data %>% group_by(city_id) %>% mutate(turncoef.2lag = lag(turnout.coef, 2))

full.data <- full.data %>% group_by(city_id) %>% mutate(urvoteshare.1lag = lag(ur.voteshare))
full.data <- full.data %>% group_by(city_id) %>% mutate(urvoteshare.2lag = lag(ur.voteshare, 2))

##Elections since treatment

full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(cancel.year.mod)==T, 0, ifelse(cancel.year.mod <= 2007 & year.x == 2008, 1, ifelse(cancel.year.mod <= 2007 & year.x == 2011, 2, ifelse(cancel.year.mod <= 2007 & year.x == 2012, 3, NA)))))

full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(elex.since.treatment) == F, elex.since.treatment, 
                                  ifelse(cancel.year.mod == 2008 & year.x < 2011, 0, 
                                  ifelse(cancel.year.mod == 2008 & year.x == 2011, 1,
                                  ifelse(cancel.year.mod == 2008 & year.x == 2012, 2, elex.since.treatment)))))


full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(elex.since.treatment) == F, elex.since.treatment, 
                                  ifelse(cancel.year.mod > 2008 & cancel.year.mod <= 2011 & year.x <= 2011, 0, 
                                  ifelse(cancel.year.mod > 2008 & cancel.year.mod <= 2011 & year.x == 2012, 1,  elex.since.treatment))))


full.data <- full.data %>% mutate(elex.since.treatment = ifelse(is.na(elex.since.treatment) == F, elex.since.treatment, 0))

##Region id as factor

full.data <- full.data %>% mutate(regionid.ch = as.factor(regionid.ch))
```

Weights

city_id_factor + presidential + xconst.lag + putin.app.3mo +  urgov + 
                 mayor.tenure +  lnAvgSalary + dem + comp.scale2  + known.opp.mayor + margin.most.recent

```{r}
##Note: including urvoteshare and/or turnoutcoef worsens balance on those variables, so they are excluded

covariates <- full.data %>% select(city_id, presidential, xconst.lag, putin.app.3mo, urgov, mayor.tenure, lnAvgSalary, dem, comp.scale2, known.opp.mayor, margin.most.recent, year.x, treated.mod, turnout.coef, years.under.regime, ur.voteshare , treated.mod.1lag, treated.mod.2lag, treated.mod.3lag, years.with.elections, urvoteshare.1lag, turncoef.1lag)
                                   
complete.tf <- complete.cases(covariates)
covariates <- bind_cols(covariates, complete.tf)
covariates <- covariates %>% dplyr::rename(complete.tf = ...23)

covariates <- covariates %>% filter(complete.tf == T)

data_long_sort <- covariates %>% dplyr::arrange(city_id, year.x)
data_long_sort <- data_long_sort %>% dplyr::select(-complete.tf)
data_long_sort <- data.frame(data_long_sort)

w <- ipwtm(
  exposure = treated.mod,
  family = "binomial",
  link = "logit",
  numerator = ~ treated.mod.1lag + treated.mod.2lag,
  denominator = ~ treated.mod.1lag + treated.mod.2lag + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent +  dem  + years.with.elections + urvoteshare.1lag + turncoef.1lag,
  id = city_id,
  timevar=year.x,
  type="first",
  data = data_long_sort)
summary(w$ipw.weights)
```

```{r}
iptw = w$ipw.weights


# Add the iptw variable onto a new dataframe = data2.
data2 <- cbind(data_long_sort, iptw)

##Truncated weights .95

data2 <- data2 %>% mutate(tsw = ifelse(iptw < quantile(iptw, probs=.05), quantile(iptw, probs=.05), iptw))

data2 <- data2 %>% mutate(tsw = ifelse(iptw > quantile(iptw, probs=.95), quantile(iptw, probs=.95), tsw))

summary(data2$tsw)

###########################################################################################
# Plot the stablized inverse probability weights
###########################################################################################
# We look for any variation from a neutral value. If there are not much variations, the IPTW is stable.
ipwplot(weights = data2$iptw, 
        timevar = data2$year.x, 
        binwidth = 0.5,
        main = "Stabilized weights", 
        xaxt = "n",
        yaxt = "n")


ipwplot(weights = data2$tsw, 
        timevar = data2$year.x, 
        binwidth = 0.5,
        main = "Stabilized weights", 
        xaxt = "n",
        yaxt = "n", ylim =c(-0.0925, .1305))

p <- ggplot(data2, aes(x=as.factor(year.x), y=tsw)) + 
  geom_boxplot() + geom_hline(yintercept = 1, linetype=2) + xlab("Year") + ylab("Truncated weights") + theme_bw()
p
```

Balance

```{r}

cobalt::bal.tab(treated.mod ~ data2, data =  data2)

cobalt::bal.tab(treated.mod ~ data2, data =  data2, weights = "iptw")

cobalt::bal.tab(treated.mod ~ data2, data =  data2, weights = "tsw")
```



Models

```{r}
###########################################################################################
# confint.geeglm function (to generate 95% CI for the geeglm())
###########################################################################################
confint.geeglm <- function(object, parm, level = 0.95, ...) {
  cc <- coef(summary(object))
  mult <- qnorm((1+level)/2)
  citab <- with(as.data.frame(cc),
                cbind(lwr=Estimate-mult*Std.err,
                      upr=Estimate+mult*Std.err))
  rownames(citab) <- rownames(cc)
  citab[parm,]
}


###########################################################################################
# GEE model #1.1 - GEE with cluster robust SE (no IPTW)
###########################################################################################
gee.bias <- geeglm(turnout.coef~ treated.post.treatment +  presidential + xconst.lag +
                     putin.app.3mo + years.under.regime + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1")
summary(gee.bias)
confint.geeglm(gee.bias, level=0.95)
```

```{r}
###########################################################################################
# GEE model #2 - IPTW fitted to MSM with clustered robust SE
###########################################################################################
########################################################################
gee.iptw <- geeglm(turnout.coef~ treated.mod + treated.mod.1lag + treated.mod.2lag + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw)
#m1 <- broom::tidy(gee.iptw)
#pixiedust::dust(m1) %>%
#  pixiedust::sprinkle_print_method("html")


gee.iptw2 <- geeglm(ur.voteshare~ treated.mod + treated.mod.1lag + treated.mod.2lag +  presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + turnout.coef + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw2)

#m2 <- broom::tidy(gee.iptw2)
#pixiedust::dust(m2) %>%
#  pixiedust::sprinkle_print_method("html")

sjPlot::tab_model(gee.iptw, gee.iptw2, show.ci = F, p.style = "stars", digits = 3, show.se = T, collapse.se =  T)

```


###Without lagged voteshare and tc


```{r}
##Note: including urvoteshare and/or turnoutcoef worsens balance on those variables, so they are excluded

covariates <- full.data %>% select(city_id, presidential, xconst.lag, putin.app.3mo, urgov, mayor.tenure, lnAvgSalary, dem, comp.scale2, known.opp.mayor, margin.most.recent, year.x, treated.mod, turnout.coef, years.under.regime, ur.voteshare , treated.mod.1lag, treated.mod.2lag, treated.mod.3lag, years.with.elections)
                                   
complete.tf <- complete.cases(covariates)
covariates <- bind_cols(covariates, complete.tf)
covariates <- covariates %>% dplyr::rename(complete.tf = ...21)

covariates <- covariates %>% filter(complete.tf == T)

data_long_sort <- covariates %>% dplyr::arrange(city_id, year.x)
data_long_sort <- data_long_sort %>% dplyr::select(-complete.tf)
data_long_sort <- data.frame(data_long_sort)

w <- ipwtm(
  exposure = treated.mod,
  family = "binomial",
  link = "logit",
  numerator = ~ treated.mod.1lag + treated.mod.2lag + treated.mod.3lag,
  denominator = ~ treated.mod.1lag + treated.mod.2lag + treated.mod.3lag +  urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections,
  id = city_id,
  timevar=year.x,
  type="first",
  data = data_long_sort)
summary(w$ipw.weights)
```

```{r}
iptw = w$ipw.weights


# Add the iptw variable onto a new dataframe = data2.
data2 <- cbind(data_long_sort, iptw)

##Truncated weights .95

data2 <- data2 %>% mutate(tsw = ifelse(iptw < quantile(iptw, probs=.05), quantile(iptw, probs=.05), iptw))

data2 <- data2 %>% mutate(tsw = ifelse(iptw > quantile(iptw, probs=.95), quantile(iptw, probs=.95), tsw))

summary(data2$tsw)

###########################################################################################
# Plot the stablized inverse probability weights
###########################################################################################
# We look for any variation from a neutral value. If there are not much variations, the IPTW is stable.
ipwplot(weights = data2$iptw, 
        timevar = data2$year.x, 
        binwidth = 0.5,
        main = "Stabilized weights", 
        xaxt = "n",
        yaxt = "n")


ipwplot(weights = data2$tsw, 
        timevar = data2$year.x, 
        binwidth = 0.5,
        main = "Stabilized weights", 
        xaxt = "n",
        yaxt = "n")
```

Balance

```{r}

cobalt::bal.tab(treated.mod ~ data2, data =  data2)

cobalt::bal.tab(treated.mod ~ data2, data =  data2, weights = "iptw")

cobalt::bal.tab(treated.mod ~ data2, data =  data2, weights = "tsw")
```



Models

```{r}
###########################################################################################
# confint.geeglm function (to generate 95% CI for the geeglm())
###########################################################################################
confint.geeglm <- function(object, parm, level = 0.95, ...) {
  cc <- coef(summary(object))
  mult <- qnorm((1+level)/2)
  citab <- with(as.data.frame(cc),
                cbind(lwr=Estimate-mult*Std.err,
                      upr=Estimate+mult*Std.err))
  rownames(citab) <- rownames(cc)
  citab[parm,]
}


###########################################################################################
# GEE model #1.1 - GEE with cluster robust SE (no IPTW)
###########################################################################################
gee.bias <- geeglm(turnout.coef~ treated.post.treatment +  presidential + xconst.lag +
                     putin.app.3mo + years.under.regime + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1")
summary(gee.bias)
confint.geeglm(gee.bias, level=0.95)
```

```{r}
###########################################################################################
# GEE model #2 - IPTW fitted to MSM with clustered robust SE
###########################################################################################
########################################################################
gee.iptw <- geeglm(turnout.coef~ treated.mod + treated.mod.1lag + treated.mod.2lag + treated.mod.3lag + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw)
m1 <- broom::tidy(gee.iptw)
pixiedust::dust(m1) %>%
  pixiedust::sprinkle_print_method("html")


gee.iptw2 <- geeglm(ur.voteshare~ treated.mod + treated.mod.1lag + treated.mod.2lag + treated.mod.3lag + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + turnout.coef + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw2)

m2 <- broom::tidy(gee.iptw2)
pixiedust::dust(m2) %>%
  pixiedust::sprinkle_print_method("html")
```


###Cumulative treatment

```{r}
##Note: including urvoteshare and/or turnoutcoef worsens balance on those variables, so they are excluded

covariates <- full.data %>% select(city_id, presidential, xconst.lag, putin.app.3mo, urgov, mayor.tenure, lnAvgSalary, dem, comp.scale2, known.opp.mayor, margin.most.recent, year.x, treated.mod, turnout.coef, years.under.regime, ur.voteshare , years.with.elections, urvoteshare.1lag, turncoef.1lag, elex.since.treatment)
                                   
complete.tf <- complete.cases(covariates)
covariates <- bind_cols(covariates, complete.tf)
covariates <- covariates %>% dplyr::rename(complete.tf = ...21)

covariates <- covariates %>% filter(complete.tf == T)

data_long_sort <- covariates %>% dplyr::arrange(city_id, year.x)
data_long_sort <- data_long_sort %>% dplyr::select(-complete.tf)
data_long_sort <- data.frame(data_long_sort)

w <- ipwtm(
  exposure = treated.mod,
  family = "binomial",
  link = "logit",
  numerator = ~ 1,
  denominator = ~ urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + dem  + years.with.elections +  urvoteshare.1lag + turncoef.1lag,
  id = city_id,
  timevar=year.x,
  type="first",
  data = data_long_sort)
summary(w$ipw.weights)
```

```{r}
iptw = w$ipw.weights


# Add the iptw variable onto a new dataframe = data2.
data2 <- cbind(data_long_sort, iptw)

##Truncated weights .95

data2 <- data2 %>% mutate(tsw = ifelse(iptw < quantile(iptw, probs=.05), quantile(iptw, probs=.05), iptw))

data2 <- data2 %>% mutate(tsw = ifelse(iptw > quantile(iptw, probs=.95), quantile(iptw, probs=.95), tsw))

summary(data2$tsw)

###########################################################################################
# Plot the stablized inverse probability weights
###########################################################################################
# We look for any variation from a neutral value. If there are not much variations, the IPTW is stable.
ipwplot(weights = data2$iptw, 
        timevar = data2$year.x, 
        binwidth = 0.5,
        main = "Stabilized weights", 
        xaxt = "n",
        yaxt = "n")


ipwplot(weights = data2$tsw, 
        timevar = data2$year.x, 
        binwidth = 0.5,
        main = "Stabilized weights", 
        xaxt = "n",
        yaxt = "n")
```


```{r}
###########################################################################################
# GEE model #2 - IPTW fitted to MSM with clustered robust SE
###########################################################################################
########################################################################
gee.iptw <- geeglm(turnout.coef~ elex.since.treatment + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw)
#m1 <- broom::tidy(gee.iptw)
#pixiedust::dust(m1) %>%
#  pixiedust::sprinkle_print_method("html")


gee.iptw2 <- geeglm(ur.voteshare~ elex.since.treatment + presidential + xconst.lag +
                     putin.app.3mo + mayor.tenure + turnout.coef + cluster(city_id),
                    id=city_id,
                    data=data2, 
                    family=gaussian("identity"), 
                    corstr="ar1", 
                   weights=tsw)
summary(gee.iptw2)

#m2 <- broom::tidy(gee.iptw2)
#pixiedust::dust(m2) %>%
#  pixiedust::sprinkle_print_method("html")
```


###Generating weights using CBPM

Not working even when cities with missing values for any year are excluded to create a balanced panel (using filter(city_id %in% (unique(covariates$xxxx))==F))
--Solve this problem, you need to code the years as periods (i.e. 2003 == 1, 2004 == 2, etc.)

This works as far as running the code goes, but does not actually produce weights (they show up as NA)

+ known.opp.mayor + margin.most.recent + dem + years.with.elections + urvoteshare.1lag + turncoef.1lag + urgov + dem + margin.most.recent

```{r}
full.data <- full.data %>% mutate(treated.mod = as.factor(treated.mod))
full.data <- full.data %>% mutate(time = ifelse(year.x == 2004, 1, ifelse(year.x == 2007, 2, ifelse(year.x == 2008, 3, ifelse(year.x == 2011, 4, 5)))))


form1 <- "treated.mod.fix ~ lnAvgSalary + comp.scale2"

cpbs.model <- CBPS::CBMSM(formula = form1, id = covariatesnew2$city_id, time = covariatesnew2$time, data = covariatesnew2, type = "MSM", twostep = T, time.vary = F)

bal1 <- CBPS::balance(cpbs.model)

plot(cpbs.model)
```

Trying with WeightIt


To do this, need to capture the full treatment history. I.e. tx1 = 1 if treated in 2003, tx2 = 1 if treated in 2004

```{r}
#full.data <- full.data %>% mutate(tx1 = 0)
#full.data <- full.data %>% mutate(tx2 = 0)
full.data <- full.data %>% mutate(tx3 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2007, 1, 0)))
full.data <- full.data %>% mutate(tx4 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2007, 1, 0)))
full.data <- full.data %>% mutate(tx5 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2011, 1, 0)))
full.data <- full.data %>% mutate(tx6 = ifelse(is.na(cancel.year) == T, 0, ifelse(cancel.year <= 2011, 1, 0)))



```


```{r}
W <- weightitMSM(list(tx3 ~ urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections,
                      #tx2 ~ tx1 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections,
                    
                      tx4 ~ tx3 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections,
                      tx5 ~  +  tx3  + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections,
                      tx6 ~ tx3 + tx4 + tx5 + urgov + lnAvgSalary + comp.scale2 + known.opp.mayor +  margin.most.recent + margin.most.recent + dem  + years.with.elections),
                 method = "cbps",
                      data = full.data)
```

