---
title: "Appointed vs elected mayors in Russia"
output: html_notebook
---


```{r setup}
library(readxl)
library(tidyverse)
library(CBPS)
library(lmtest)  #Getting clustered sEs 
library(sandwich)
library(ggplot2)
library(stargazer)

full.data <- read.csv("coefs with city covariates.csv")

full.data <- full.data %>% mutate(treat.running = ifelse(year.x <= 2004, 0, ifelse(year.x <= 2007 & (treat.group.08 == 1 | treat.group.07 == 1), 1, ifelse(treat.group.12 == 1 | treat.group.11 == 1, 1, 0))))

full.data.0308 <- subset(full.data, full.data$year.x <= 2008)
full.data.0308 <- full.data.0308 %>% filter(is.na(cancel.year) == TRUE | cancel.year >= 2003)
full.data.0308 <- full.data.0308 %>% mutate(treat.group.0308 = ifelse(is.na(cancel.year == TRUE), 0, 
                                                                      ifelse(cancel.year < 2008, 1, 0)))
full.data.0308 <- full.data.0308 %>% mutate(post.treat.0308 = ifelse(year.x == 2007 | year.x == 2008, 1, 0))

full.data.0712 <- subset(full.data, full.data$year.x >= 2007)
full.data.0712 <- full.data.0712 %>% filter(is.na(cancel.year) == TRUE | cancel.year > 2008)
full.data.0712 <- full.data.0712 %>% mutate(treat.group.0712 = ifelse(is.na(cancel.year == TRUE), 0, 
                                                                      ifelse(cancel.year <= 2010, 1, 0)))
full.data.0712 <- full.data.0712 %>% mutate(post.treat.0712 = ifelse(year.x == 2011 | year.x == 2012, 1, 0))

full.data.0312 <- subset(full.data, full.data$year.x <= 2004 | full.data$year.x > 2008)
full.data.0312 <- full.data.0312 %>% filter(is.na(cancel.year) == TRUE | cancel.year > 2008)
full.data.0312 <- full.data.0312 %>% mutate(treat.group.0312 = ifelse(is.na(cancel.year == TRUE), 0, 
                                                                      ifelse(cancel.year > 2008 & cancel.year <= 2010, 1, 0)))
full.data.0312 <- full.data.0312 %>% mutate(post.treat.0312 = ifelse(year.x == 2011 | year.x == 2012, 1, 0))

###Correcting coding errors below

full.data <- full.data %>% mutate(treatment.group = ifelse(city_id == 90 | city_id == 176, 1, treatment.group))
full.data <- full.data %>% mutate(treatment.group = ifelse(city_id == 175, 0, treatment.group))

```

Example plot for nonstandard coefficient

```{r}
penza <- read.csv("penza2011.csv")
armavir <- read.csv("armavir2011.csv")

penza <- penza %>% mutate(regionname = "Penza")
armavir <- armavir %>% mutate(regionname = "Armavir")

regions.data <- rbind(penza, armavir)
regions.data <- regions.data %>% mutate(regionname = factor(regionname))

p.nonstandard <- ggplot(regions.data, aes(pct.nonstandard, ur.abshare)) + geom_point() + facet_grid(cols = vars(regionname)) + geom_smooth(se = FALSE, method = lm)

p.nonstandard + labs(x = "Percent nonstandard", y = "UR absolute vote-share") + theme_bw()

```


Example plot for turnout coefficient

```{r}
volgodonsk <- read.csv("Volgodonsk2011.csv")
novgorod <- read.csv("VelikijNovgorod2011.csv")

volgodonsk <- volgodonsk %>% mutate(regionname = "Volgodonsk")
novgorod <- novgorod %>% mutate(regionname = "Velikij Novgorod")

regions.data <- rbind(volgodonsk, novgorod)
regions.data <- regions.data %>% mutate(regionname = factor(regionname))

p.nonstandard <- ggplot(regions.data, aes(turnout, ur.abshare)) + geom_point() + facet_grid(cols = vars(regionname)) + geom_smooth(se = FALSE, method = lm)

p.nonstandard + theme_bw()

```



##Covariate balancing propensity score models for 2003-2008

Selection model and balance statistics

'margin' refers to the mayor's most recent margin of victory at a given year

'regelect_margin' refers to United Russia's vote-share in the most recent legislative election in the mayor's city under that mayor


Note that CBPS package has a longitudinal data version (CBMSM), but it does not cooperate with this data--throws an error 'replacement has length zero'

```{r}
form0 <- "d.gone.neg ~ d.gone.neg.l1 + camp.length"
fit0<-CBMSM(formula = form0, time=Blackwell$time,id=Blackwell$demName,
data=Blackwell, type="MSM", iterations = NULL, twostep = TRUE,
msm.variance = "approx", time.vary = FALSE)
```

```{r}
#full.data.0308 <- full.data.0308 %>% mutate(cbps.treat.0708 =   ifelse(treat.group.0308 == 1 & year.x >= 2007, 1, 0))

myvars <- c("city_id", "nonstandard.coef",  "treat.running",
                "ethnic.categorical",  "urgov", "margin", "mayor.tenure",
                 "lnAvgSalary",  "unemployrate",  "dem", "regelect_margin",  "education", "presidential", "poppopprop", "regmarginXmargin", "year.x", "PositionCity")
   
dataset.matching <- full.data[myvars]
dataset.matching.complete <- na.omit(dataset.matching)
#dataset.matching.complete <- dataset.matching.complete %>% mutate(time = ifelse(year.x == 2003, 1, ifelse(year.x == 2004, 2, ifelse(year.x == 2007, 3, 4))))

form0 <-  "treat.running ~ margin + dem + regelect_margin +
                  poppopprop + mayor.tenure + lnAvgSalary + regmarginXmargin"  
cbps.out.0308 <- CBMSM(form0, data=dataset.matching.complete, time = dataset.matching.complete$year.x, id = dataset.matching.complete$PositionCity)
```

##Cross section versions below


```{r}
full.data.0308 <- full.data.0308 %>% mutate(cbps.treat.0708 =   ifelse(treat.group.0308 == 1 & year.x >= 2007, 1, 0))

myvars <- c("city_id", "nonstandard.coef",  "cbps.treat.0708",
                "ethnic.categorical",  "urgov", "margin", "mayor.tenure",
                 "lnAvgSalary",  "unemployrate",  "dem", "regelect_margin",  "education", "presidential", "poppopprop", "regmarginXmargin", "year.x")
   
dataset.matching <- full.data.0308[myvars]
dataset.matching <- dataset.matching %>% filter(year.x >= 2007)
dataset.matching.complete <- na.omit(dataset.matching)
   
cbps.out.0308 <- CBPS(cbps.treat.0708 ~ margin + dem + regelect_margin +
                        poppopprop + mayor.tenure + lnAvgSalary + regmarginXmargin, data=dataset.matching.complete)
summary(cbps.out.0308)
oversight.bal.firstround <- CBPS::balance(cbps.out.0308)
oversight.bal.firstround

pct.improvement.round1 <- abs((oversight.bal.firstround$balanced[,1] - oversight.bal.firstround$original[,1])/oversight.bal.firstround$original[,1])
```

Second-stage model using CBPS weights



```{r}
cbpsmodel0308 <- lm(nonstandard.coef ~ cbps.treat.0708 + ethnic.categorical
                   + urgov + #margin +
                     mayor.tenure + lnAvgSalary + regelect_margin +
                     unemployrate +  #dem +  
                     education +
                     presidential, 
                      weights=cbps.out.0308$weights,
                      data = cbps.out.0308$data)
summary(cbpsmodel0308)



coeftest.results.0308 <- coeftest(cbpsmodel0308, vcov = vcovCL(cbpsmodel0308, type="HC1", cluster = cbps.out.0308$data$city_id)) ##vcovCL is for clustered SEs, type is correct for lm models
coeftest.results.0308


```

##CBPS models for 2007-2012

Selection model

```{r}
full.data.0712 <- full.data.0712 %>% mutate(cbps.treat.1112 = ifelse(treat.group.0712 == 1 & year.x >= 2011, 1, 0))
   myvars <- c("city_id", "nonstandard.coef",  "cbps.treat.1112",
                "ethnic.categorical",  "urgov", "margin", "mayor.tenure",
                 "lnAvgSalary",  "unemployrate",  "dem", "regelect_margin",  "education", "presidential", "poppopprop", "regmarginXmargin", "year.x")
   
   
dataset.matching <- full.data.0712[myvars]
dataset.matching <- dataset.matching %>% filter(year.x >= 2011)
dataset.matching.complete <- na.omit(dataset.matching)
   
cbps.out.0712 <- CBPS(cbps.treat.1112 ~ margin + dem + regelect_margin +
                        poppopprop + mayor.tenure + lnAvgSalary + regmarginXmargin, data=dataset.matching.complete)

summary(cbps.out.0712)
oversight.bal.secondround <- CBPS::balance(cbps.out.0712)
oversight.bal.secondround

pct.improvement.round2 <- abs((oversight.bal.secondround$balanced[,1] - oversight.bal.secondround$original[,1])/oversight.bal.secondround$original[,1])
```


Second-stage model

```{r}
cbpsmodel0712 <- lm(nonstandard.coef ~ cbps.treat.1112 + ethnic.categorical
                   + urgov + #margin +
                     mayor.tenure + lnAvgSalary + regelect_margin +
                     unemployrate +  #dem +  
                     education +
                     presidential, 
                      weights=cbps.out.0712$weights,
                      data = cbps.out.0712$data)
summary(cbpsmodel0712)
   
coeftest.results.0712 <- coeftest(cbpsmodel0712, vcov = vcovCL(cbpsmodel0712, type="HC1", cluster = cbps.out.0712$data$city_id))

coeftest.results.0712
```

##CBPS models for 2003-2012

Selection model without vars with high missingness

```{r}

#full.data <- full.data %>% mutate(cbps.treat.1112 = ifelse(treatment.group == 1 & year.x >= 2011, 1, 0))


myvars <- c("city_id", "nonstandard.coef",  "treatment.group",
                "ethnic.categorical",  "urgov", "margin", 
            "mayor.tenure",
                 "lnAvgSalary",  "unemployrate",  "dem", "regelect_margin",
            "education", "presidential", "poppopprop", "year.x", "regmarginXmargin")
   
   
dataset.matching <- full.data[myvars]
dataset.matching <- dataset.matching %>% filter(year.x >= 2011)
dataset.matching.complete <- na.omit(dataset.matching)
   
cbps.out.0312 <- CBPS(treatment.group ~ margin + dem + regelect_margin +
                        
                      poppopprop + mayor.tenure + lnAvgSalary +regmarginXmargin
                        , data=dataset.matching.complete)
summary(cbps.out.0312)

oversight.bal.all <- CBPS::balance(cbps.out.0312)

pct.improvement.all <- abs((oversight.bal.all$balanced[,1] - oversight.bal.all$original[,1])/oversight.bal.all$original[,1])
```

```{r}

cbpsmodel0312 <- lm(nonstandard.coef ~ treatment.group + ethnic.categorical
                   + urgov + #margin +
                     mayor.tenure + lnAvgSalary + regelect_margin +
                     unemployrate +  dem +  
                     education +
                     presidential, 
                      weights=cbps.out.0312$weights,
                      data = cbps.out.0312$data)
summary(cbpsmodel0312)
   
coeftest(cbpsmodel0312, vcov = vcovCL(cbpsmodel0312, type="HC1", cluster = cbps.out.0312$data$city_id))
```


Full selection model with lots of missingness (results in few treatment obs)

```{r}

full.data <- full.data %>% mutate(cbps.treat.1112 = ifelse(treatment.group == 1 & year.x >= 2011, 1, 0))

full.data.0312 <- subset(full.data, full.data$year.x <= 2004 | full.data$year.x > 2008)

myvars <- c("city_id", "nonstandard.coef",  "cbps.treat.1112",
                "ethnic.categorical",  "urgov", "margin", 
            "mayor.tenure",
                 "lnAvgSalary",  "unemployrate", "dem", "regelect_margin",
            "education", "presidential", "poppopprop", "regmarginXmargin")
   
   
dataset.matching <- full.data.0312[myvars]
dataset.matching.complete <- na.omit(dataset.matching)
   
cbps.out.0312 <- CBPS(cbps.treat.1112 ~ margin + dem + regelect_margin +
                        poppopprop + mayor.tenure + lnAvgSalary+ 
                        regmarginXmargin
                        , data=dataset.matching.complete)
summary(cbps.out.0312)

oversight.bal.all <- balance(cbps.out.0312)

pct.improvement.all <- (oversight.bal.all$balanced[,1] - oversight.bal.all$original[,1])/oversight.bal.all$original[,1]
```


```{r}

cbpsmodel0312 <- lm(nonstandard.coef ~ cbps.treat.1112 + ethnic.categorical
                   + urgov + margin +
                     mayor.tenure + lnAvgSalary + regelect_margin +
                     unemployrate +  dem +  
                     education +
                     presidential, 
                      weights=cbps.out.0312$weights,
                      data = cbps.out.0312$data)
summary(cbpsmodel0312)
   
coeftest(cbpsmodel0312, vcov = vcovCL(cbpsmodel0312, type="HC1", cluster = cbps.out.0312$data$city_id))
```


##Tables for CBPS balance and outcomes

```{r}
pct.improvement.combined <- matrix(NA, nrow = 7, ncol = 3)
pct.improvement.combined[,1] <- names(pct.improvement.round1)
pct.improvement.combined[,2] <- round(pct.improvement.round1, 4)
pct.improvement.combined[,3] <- round(pct.improvement.round2, 4)
stargazer(pct.improvement.combined, type="html", out = "balance improvement.html")
```

```{r}
stargazer(coeftest.results.0308, coeftest.results.0712, type="html", out = "outcome models.html")
```


##Difference in differences models

2003-2008

```{r}
didmodel03 <- lm(nonstandard.coef ~ treat.group.0308 + post.treat.0308 +
                   ethnic.categorical
                   + urgov + #margin +
                     mayor.tenure + lnAvgSalary + #regelect_margin +
                     unemployrate +  dem +  
                     education +
                     presidential +
                 treat.group.0308*post.treat.0308, data=full.data.0308)
summary(didmodel03)

#coeftest(didmodel03, vcov = vcovCL(didmodel03, type="HC1", cluster = full.data.0308$city_id.y))
```

2007-2012

```{r}
didmodel07 <- lm(nonstandard.coef ~ treat.group.0712 + post.treat.0712 +
                   ethnic.categorical
                   + urgov + #margin +
                     mayor.tenure + lnAvgSalary + #regelect_margin +
                     unemployrate +  dem +  
                     education +
                     presidential +
                 treat.group.0712*post.treat.0712, data=full.data.0712)
summary(didmodel07)
```


```{r}
full.data.0312 <- full.data.0312 %>% mutate(city_id = factor(city_id))

didmodel0312 <- lm(nonstandard.coef ~ treatment.group + post.treat.0312 +
                   ethnic.categorical
                   + urgov + #margin +
                     mayor.tenure + lnAvgSalary + #regelect_margin +
                     unemployrate +  dem +  
                     education +
                     presidential +
                 treatment.group*post.treat.0312, data=full.data.0312)
summary(didmodel0312)


```
