---
title: "R Notebook"
output: html_notebook
---

##Setup and balance##

```{r setup}
library(readxl)
library(tidyverse)
library(CBPS)
library(lmtest)  #Getting clustered sEs 
library(sandwich)
library(ggplot2)
library(stargazer)
library(interplot)
library(eventStudy)
library(data.table)
library(cobalt) #Balance; very useful package
```


```{r}
full.data <- read.csv("cleaned data full all years.csv")


full.data <- full.data %>% mutate(years.since.treat = ifelse(is.na(cancel.year) == TRUE | cancel.year > year.x, 0, (year.x - cancel.year) + 1))

#full.data <- full.data %>% mutate(treat.weight.year = ifelse(treated.0708 == 1, treated.0708 / years.since.treat, 0))

full.data <- full.data %>% mutate(years_with_elections = ifelse(is.na(cancel.year) == TRUE, year.x - 2003, year.x - cancel.year))

full.data <- full.data %>% mutate(turnout.coef.susp = ifelse(turnout.coef >= 1, 1, 0))


full.data <- full.data %>% mutate(election.period = ifelse(year.x == 2003, 1, ifelse(year.x == 2004, 2, ifelse(year.x
                                  == 2007, 3, ifelse(year.x == 2008, 4,
                                  ifelse(year.x == 2011, 5, 6))))))

full.data <- full.data %>% mutate(treat.cohort = ifelse(is.na(cancel.year) == TRUE, "Inf", ifelse(cancel.year >= 2004 &                                                  cancel.year < 2007, 2, ifelse(
                                                 cancel.year == 2007, 3, ifelse(
                                                   cancel.year >= 2008 & cancel.year < 2011, 4, ifelse(
                                                     cancel.year == 2011, 5, "Inf"
                                                   )
                                                 )
))))



#full.data <- full.data %>% mutate(rel.treat.time = ifelse(treat.cohort == "Inf", 0, time.period - as.numeric(treat.cohort)))

full.data <- full.data %>% mutate(treat.cohort = factor(treat.cohort))

#Next make individual variables for each level of the factor; also try the same approach with only three periods (year <= 2004 = 0, year <=2008 = 1, year <= 2012 = 2)




full.data <- full.data %>% mutate(cohort2 = ifelse(as.numeric(treat.cohort) == 2, 1, 0))
full.data <- full.data %>% mutate(cohort3 = ifelse(as.numeric(treat.cohort) == 3, 1, 0))
full.data <- full.data %>% mutate(cohort4 = ifelse(as.numeric(treat.cohort) == 4, 1, 0))
full.data <- full.data %>% mutate(cohort5 = ifelse(as.numeric(treat.cohort) == 5, 1, 0))
full.data <- full.data %>% mutate(cohort_inf = ifelse(treat.cohort == "Inf", 1, 0))

full.data <- full.data %>% mutate(appointed.exec = ifelse(treated.0708 == 1 | treated.1112, 1, 0))
#full.data <- full.data %>% mutate(appointed.exec = ifelse(year.x == 2003, NA, appointed.exec))

full.data <- full.data %>% mutate(elected.transition = ifelse(year.x < cancel.year & exec.first.election == 1, 1, 0))
full.data <- full.data %>% mutate(appointed.transition = ifelse(year.x >= cancel.year & cross.regime.transition == 0 & exec.first.election == 1, 1, 0))


full.data <- 
    full.data %>%
    group_by(city_id) %>%
    mutate(lag.manipulation = dplyr::lag(turnout.coef, n = 1, default = NA)) #Lagging manipulation

```

Creating relative treatment counter using time.period instead of calendar time
Time periods are:
2003 == 1
2004 == 2
2007 == 3
2008 == 4
2011 == 5
2012 == 6

Treatment period should collapse to the previous election time. I.e. elections canceled between 2004 and 2007 should score as 2, so that they are 1 period post treatment by 2007 election

```{r}
full.data <- full.data %>% mutate(cancel.period = ifelse(is.na(cancel.year) == TRUE, NA, ifelse(
  cancel.year < 2007, 3, ifelse(
    cancel.year == 2007, 4, ifelse(
      cancel.year > 2007 & cancel.year < 2011, 5, ifelse(
        cancel.year == 2011, 6, NA
      )
    ) 
  )
)))

#full.data <- full.data %>% mutate(rel.treat.period = ifelse())
```

```{r}
full.data <- full.data %>% mutate(election.period = as.integer(election.period))
full.data <- full.data %>% mutate(cancel.period = as.integer(cancel.period))

full.data.table <- data.table(full.data)

full.data <- full.data %>% mutate(rel.treat.time = ifelse(is.na(cancel.period) == TRUE, -1, election.period - cancel.period))


full.data <- full.data %>%
  mutate(rel.treat.time2 = rel.treat.time)

full.data <- full.data %>%
  mutate(value = 1,
         rel.treat.time2 = paste0("rel.time", rel.treat.time2)) %>%
  spread(rel.treat.time2, value, fill = 0)


full.data <- full.data %>% mutate(cohort1 = ifelse(cancel.period == 1, 1, 0))
full.data <- full.data %>% mutate(cohort2 = ifelse(cancel.period == 2, 1, 0))
full.data <- full.data %>% mutate(cohort3 = ifelse(cancel.period == 3, 1, 0))
full.data <- full.data %>% mutate(cohort4 = ifelse(cancel.period == 4, 1, 0))
full.data <- full.data %>% mutate(cohort5 = ifelse(cancel.period == 5, 1, 0))
full.data <- full.data %>% mutate(cohort6 = ifelse(cancel.period == 6, 1, 0))
full.data <- full.data %>% mutate(cohort.untreat = ifelse(is.na(cancel.period) == T, 1, 0))


full.data <- full.data %>%
  mutate(ethnic.categorical2 = ethnic.categorical)

full.data <- full.data %>%
  mutate(value = 1,
         ethnic.categorical2 = paste0("ethcat", ethnic.categorical2)) %>%
  spread(ethnic.categorical2, value, fill = 0)

```


Looking at balance; there isn't much difference on any of these dimensions except 'dem'.

```{r}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


```{r}
###Untreated vs. early treated
treated.obs1 <- full.data %>% filter(year.x <= 2008)
covs <- treated.obs1  %>% dplyr::select(nonstandard.coefs03, ur.coef.2003, ur.voteshare.2003,
                             nonstandard.coefs04, ur.coef.2004, ur.voteshare.2004, dem, civsoc91,
                             kprf99, education, pctRussian2002_new, opp_mayor1)
bal.tab(covs, treat = treated.obs1$treated.0708)
p.bal.ns03 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "nonstandard.coefs03")
p.bal.ns04 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "nonstandard.coefs04")
p.bal.urc03 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.coef.2003") + labs(title = "", x = "United Russia manipulation coefficient\n (2003)")
p.bal.urc04 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.coef.2004") +  labs(title = "", x = "United Russia manipulation coefficient\n (2004)")
p.bal.urvs03 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.voteshare.2003") + labs(title = "", x = "United Russia vote-share\n (2003)")
p.bal.urvs04 <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "ur.voteshare.2004") + labs(title = "", x = "United Russia vote-share\n (2004)")
p.bal.dem <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "dem")
p.bal.rus <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "pctRussian2002_new")
p.bal.opp <- bal.plot(covs, treat = treated.obs1$treated.0708, var.name = "opp_mayor1") + labs(title = "Distributional Balance for 'opposition mayor', first wave", x = "Opposition mayor")


full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.coef.2003, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.coef.2004, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.voteshare.2003, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(ur.voteshare.2004, na.rm=TRUE))
full.data %>% group_by(treated.0708)  %>% summarise(means = mean(dem, na.rm=TRUE))

###Early treated vs late treated
treated.obs2 <- full.data %>% filter(year.x >= 2007 & treated.0708 == 0 | treated.1112 == 1)
covs <- treated.obs  %>% dplyr::select(nonstandard.coefs03, ur.coef.2003, ur.voteshare.2003,
                             nonstandard.coefs04, ur.coef.2004, ur.voteshare.2004, ur.coef.2007, ur.voteshare.2007, ur.coef.2008, ur.voteshare.2008,  dem, civsoc91,
                             kprf99, education, pctRussian2002_new, opp_mayor1)
bal.tab(covs, treat = treated.obs$treated.1112)
p.bal.ns03.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "nonstandard.coefs03")
p.bal.ns04.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "nonstandard.coefs04")
p.bal.urc03.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2003")
p.bal.urc04.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2004")
p.bal.urvs03.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2003")
p.bal.urvs04.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2004")
p.bal.urc07.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2007")
p.bal.urvs07.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2007")
p.bal.urc08.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.coef.2008")
p.bal.urvs08.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "ur.voteshare.2008")
p.bal.dem.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "dem")
p.bal.rus.2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "pctRussian2002_new")
p.bal.opp2 <- bal.plot(covs, treat = treated.obs2$treated.1112, var.name = "opp_mayor1") + labs(title = "Distributional Balance for 'opposition mayor'", x = "Opposition mayor")

treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.coef.2007, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.coef.2008, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.voteshare.2007, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(ur.voteshare.2008, na.rm=TRUE))
treated.obs %>% group_by(treated.1112)  %>% summarise(means = mean(dem, na.rm=TRUE))

###Multiplotting
multiplot(p.bal.urc03, p.bal.urc04, p.bal.urvs03, p.bal.urvs04, cols= 2)

multiplot(p.bal.urc07.2, p.bal.urc08.2, p.bal.urvs07.2, p.bal.urvs08.2, cols= 2)


```


##Main 2WFE models, fraud

```{r baseline model}
twfe.tc.v2.fac <- lm(turnout.coef ~  factor(city_id) + factor(year.x) +  mayor.tenure + urgov +  lnAvgSalary +
                       unemployrate  +  education  + poppopprop + factor(years.since.treat), 
                     data = full.data)
summary(twfe.tc.v2.fac)
```

```{r baseline with lagged manipulation}
twfe.tc.v2.fac.lag <- lm(turnout.coef ~  factor(city_id) + factor(year.x) +  mayor.tenure + urgov +  lnAvgSalary +
                       unemployrate  +  education  + poppopprop + lag.manipulation + factor(years.since.treat), 
                     data = full.data)
summary(twfe.tc.v2.fac.lag)
```


###Main 2WFE models, UR voteshare

```{r}
twfe.ur.v3 <- lm(ur.voteshare ~  factor(city_id) + factor(year.x) +  mayor.tenure + urgov + lnAvgSalary +
                       unemployrate  +  education + factor(years.since.treat) + turnout.coef, data = full.data)
summary(twfe.ur.v3)
```

###Tables

```{r}
stargazer(twfe.tc.v2.fac, twfe.tc.v2.fac.lag, twfe.ur.v3, type="html", omit = c("city_id", "year.x"), out="table_main.html")
```

###Event study framework

Classic 'dynamic' model:

Manipulation

```{r}
model.tc.dyn <- lm(turnout.coef ~ factor(city_id) + factor(year.x) + `rel.time-5` + `rel.time-4` +
                        `rel.time-3` + `rel.time-2` + `rel.time-1` + rel.time1 + rel.time2 + rel.time3 
                   + urgov + mayor.tenure, data = full.data)
summary(model.tc.dyn)
```

United Russia:

```{r}
model.ur.dyn <- lm(ur.voteshare ~ factor(city_id) + factor(year.x) + `rel.time-5` + `rel.time-4` +
                        `rel.time-3` + `rel.time-2` + `rel.time-1` + rel.time1 + rel.time2 + rel.time3 
                   + urgov + mayor.tenure + turnout.coef, data = full.data)
summary(model.ur.dyn)
```

Table

```{r include = FALSE}
stargazer(model.tc.dyn, model.ur.dyn, type="html", omit = "factor", out="table_app_eventstudy.html")
```

Plot

```{r}
coefs.homog <- tidy(model.tc.dyn, conf.int = TRUE, conf.level = .90)
coefs.homog.select <- coefs.homog[129:136,]
coefs.homog.select <- coefs.homog.select %>% mutate(rel.time = c(-5, -4, -3, -2, -1, 1, 2, 3))
new.row <- c(rep(NA, 7), 0)
coefs.homog.select <- rbind(coefs.homog.select, new.row)

att.plot <- ggplot(coefs.homog.select, aes(x = rel.time, y = estimate)) + geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + labs(title = "OLS estimates of relative time to treatment\n (90% confidence intervals)", x = "Time to treatment", y = "Estimate") + theme_bw()

```


```{r}
coefs.homog <- tidy(model.ur.dyn, conf.int = TRUE, conf.level = .90)
coefs.homog.select <- coefs.homog[129:136,]
coefs.homog.select <- coefs.homog.select %>% mutate(rel.time = c(-5, -4, -3, -2, -1, 1, 2, 3))
new.row <- c(rep(NA, 7), 0)
coefs.homog.select <- rbind(coefs.homog.select, new.row)

att.plot <- ggplot(coefs.homog.select, aes(x = rel.time, y = estimate)) + geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + labs(title = "OLS estimates of relative time to treatment\n (90% confidence intervals)", x = "Time to treatment", y = "Estimate") + theme_bw()

```

